### 2012-03-30 ms.tex
Initial commit

\documentclass[letterpaper, 11pt]{article}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[left=3cm,top=3cm,right=3cm]{geometry}

\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\parindent=0cm

\title{Robust Inferences from Simply Parameterised Models}

\author{%
  Brendon~J.~Brewer$^{1}$\thanks{\tt brewer@physics.ucsb.edu}, 
  Geraint~F.~Lewis$^{2}$,
  Ross Fadely\\
  \medskip\\
  $^1$UCSB\\
  $^2$USyd
}

\begin{document}

\date{\today}

\maketitle

\begin{abstract}
We discuss the practical use of simply parameterised models in Bayesian data analysis, particularly in astronomy.
The use of simply parameterised models is problematic when they are fit to large, informative data sets, resulting in unrealistically small uncertainties on inferences. In common parlance, the formal statistical errors may be small, but the systematic errors are often large and in many cases, difficult to quantify at all. In principle, the best solution to this problem is to develop more realistic complex models that accurately describe our prior beliefs. However, this is often infeasible in practice, due to computational limitations and the difficulty of defining realistic prior distributions over high dimensional spaces. As a pragmatic alternative, we show that it is possible to reinterpret the use of simple models in a way that avoids the problem of overconfident
inferences. The key idea is to weaken the connection between the parameters and the data that is assumed in the prior probabilities. This weakening can be implemented straightforwardly using the Nested Sampling algorithm.
\end{abstract}

\section{Background on Bayesian Inference}

\begin{itemize}
\item Define terminology very carefully, present Bayes' rule \\
\item Describe the ``joint'' (parameters $\times$ data space) view of inference, describe how the form of the likelihood function is prior information \citep{caticha} \\
\item Discuss use of MCMC techniques for complex problems \\
\item Discuss the various attempts at robustness/model checking/elicitation and that stuff
\end{itemize}

\begin{equation}
p(\theta | D) \propto p(\theta) p(D|\theta)|_{D=D_{\rm obs}}
\end{equation}
The various terms in this equation have the following names and meanings.

\begin{itemize}
\item $p(\theta|D)$ is the {\it posterior distribution}
for the parameters, and is usually the goal of the calculation. It describes our
knowledge and remaining uncertainty about $\theta$ after taking into account the data. \\

\item $p(\theta)$ is the {\it prior distribution}, a probability distribution
over possible values for $\theta$ that describes our uncertainty about
$\theta$ before taking into account the data. Commonly, this is a broad
probability distribution, describing a large amount of uncertainty. \\

\item $p(D|\theta)$ is a function of
both $\theta$ and $D$ and is referred to as the {\it sampling distributions}. 
The reason for the awkward plural is that $p(D|\theta)$ is a set of probability distributions,
one for each value of $\theta$. The sampling distributions describe our prior information about how the data are connected to the parameters \citep{2008arXiv0808.0012C}. \\

\item $p(D|\theta)|_{D = D_{\rm obs}}$ is called the {\it likelihood function}.
It is obtained from the sampling distributions, with the actual data substituted in,
and is therefore a function of $\theta$ only. It describes the effects of the actual data
set that was observed on our beliefs about $\theta$: values of $\theta$ with a high
likelihood predicted the data well and will have their probability upweighted
in the posterior distribution.
\end{itemize}

\begin{figure*}
\begin{center}
\includegraphics[scale=0.5]{joint_marginal.eps}
\end{center}
\end{figure*}

\section{Advantages and Disadvantages of Simply Parameterised Models}
\begin{itemize}
\item Easy to implement \\
\item Computationally fast to get inferences - therefore can be applied on a large scale, e.g. to large samples of objects. \\
\item Easy to assign non-controversial priors over low dimensional parameter spaces \\
\end{itemize}

\section{Problems with Simply Parameterised Models}
\begin{itemize}
\item They are usually false, i.e. poor models of our actual prior beliefs. \\
\item Conditional on the simple model, you get error bars that are much too small. Small error bars on the parameters may not matter so much (since the parameters don't ``exist'' anyway), but the inferences on quantities that do ``exist'' (e.g. total flux) will still be overconfident. \\
\end{itemize}

\section{Re-Interpreting Simply Parameterised Models}

\begin{itemize}
\item Describe the hypothetical process of acknowledging the complex reality, yet describing (summarising) it by fitting a simple model to the complex one. \\
\item Show some examples of this - complex curves being approximated by lines with least squares, complex density profiles (1-D and 2-D) being fit by simple density profiles by maximising some kind of entropy.
\item Mention/derive that in the special case of fitting a complex density profile with a Gaussian, the variance(s) of the Gaussian gives the actual moment(s) of the complex profile
\item Describe how fitting a simple model can be interpreted as attempting to infer the parameters of the summarising simple model, and that therefore the parameter space is completely legitimate - it's the likelihood function that is now wrong. Data = model predictions + noise breaks down, it should be Data = simple model predictions + complexity perturbations + noise
\item Describe why qualitatively, the likelihood function should now be ``weaker'' than before
\item Describe why the old likelihood function is still (often) a good hill to climb
\end{itemize}

\begin{figure*}
\begin{center}
\includegraphics[scale=0.25]{simple_complex1.eps}
\includegraphics[scale=0.25]{simple_complex2.eps}
\includegraphics[scale=0.25]{simple_complex3.eps}
\end{center}
\end{figure*}

\section{Implementation with Nested Sampling}
\begin{itemize}
\item Describe the concept of tempering/annealing and how it almost does what we want \\
\item But we don't really know what temperature we want at the outset - NS allows us to test all in a single run
\item Introduce ``convergence plots'' and how to read them
\item Subjective temperature selection and why it's not so bad
\end{itemize}

\begin{figure*}
\begin{center}
\includegraphics[scale=0.7]{nested.eps}
\end{center}
\end{figure*}

\section{More Objective Temperature Selection}
\begin{itemize}
\item If we can generate from a prior over complex models, and then fit simple models to each sample, and also generate simulated data from the complex model, we can get an idea of the joint prior over the space of (simple parameters, data)\\
\item Approximate the joint prior over (simple parameters, data) with a tempered version of the old likelihood \\
\item Find the optimal temperature that makes the approximated joint prior as close as possible to the true one.
\end{itemize}

\section{Failure Modes}
\begin{itemize}
\item If the simple model / original likelihood function is SO BAD that optimising it takes you to the wrong place in parameter space
\end{itemize}

\section{Simple Example 1: A rotation curve}

\section{Simple Example 2: An emission line}

\section{Potential Applications}

\begin{itemize}
\item Interferometry: a common goal of interferometry is to measure the angular size of some astronomical object, when it is too small to be resolved by standard telescopes. In the case of stellar interferometry, the surface brightness profile of a star is very well modelled by a circular disc with limb darkening, so this model should be used. However, with other objects, such as the dust torii in active galactic nuclei \citep[e.g.][]{2011A&A...536A..78K}, the spatial profile is not well known. If a characteristic size, or total flux or something, is the goal of the study, then the framework of this paper is applicable.\\

\item Gravitational lensing: Modelling of gravitational lenses typically aims to infer the source surface brightness profile along with the projected mass density profile of the deflector. While sophisticated many-parameter models are feasible and are used routinely now \citep{2006MNRAS.371..983S, 2007ApJ...666..726B, 2011MNRAS.412.2521B, 2006ApJ...637..608B, 2012Natur.481..341V}, they are slow, and some are not particularly realistic anyway (rant about ``regularisation'' here). With the explosion in the number of known gravitational lens systems (ref?), population-based studies will need something faster. I have already used this approach \citep{2012arXiv1201.1677B}.

\item Galaxy Structure and Morphology: Studies of populations of galaxies are often carried out by fitting simple models such as the S{\'e}rsic \citep{Sersic1968} profile to individual galaxies. It has been demonstrated that taking into account the full uncertainties on these parameters can yield different results as compared to simply studying the distribution of the best-fit parameters \citep[e.g.][]{2011MNRAS.414.1625Y}. However, since galaxies often are not well modelled by S{\'e}rsic profiles (due to their real-world complexity), the error bars on the parameters can be severely underestimated, which is almost like just using the best-fit parameters! \\

\item Studying spectra: Measuring equivalent widths, velocity dispersions and so on from emission/absorption lines. These commonly assume a specific functional form for the spectral line profile (e.g. Gaussian), which may not be applicable.

\item Any situation with correlated noise (but a believed model), we can use this method as well (e.g. \citep{2008ApJ...686..851R}).

\item Ideas? There are surely a large number of possibilities
\end{itemize}

\section*{Acknowledgements}
Tommaso Treu, Anna Pancoast, Phil Marshall, Matthew Auger, Greg Dobler, Sebastian Hoenig

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Barnab{\`e} 
\& Koopmans}{2007}]{2007ApJ...666..726B} Barnab{\`e} M., Koopmans L.~V.~E., 2007, ApJ, 666, 726

\bibitem[\protect\citeauthoryear{Brewer 
\& Lewis}{2006}]{2006ApJ...637..608B} Brewer B.~J., Lewis G.~F., 2006, ApJ, 637, 608

\bibitem[\protect\citeauthoryear{Brewer et al.}{2011}]{2011MNRAS.412.2521B} 
Brewer B.~J., Lewis G.~F., Belokurov V., Irwin M.~J., Bridges T.~J., Evans 
N.~W., 2011, MNRAS, 412, 2521

\bibitem[\protect\citeauthoryear{Brewer et al.}{2012}]{2012arXiv1201.1677B} 
Brewer B.~J., et al., 2012, arXiv, arXiv:1201.1677

\bibitem[\protect\citeauthoryear{Caticha}{2008}]{caticha} 
Caticha A., 2008, arXiv, arXiv:0808.0012

\bibitem[\protect\citeauthoryear{Jaynes 
\& Bretthorst}{2003}]{2003prth.book.....J} Jaynes E.~T., Bretthorst G.~L., 2003, prth.book,

\bibitem[\protect\citeauthoryear{Kishimoto et 
al.}{2011}]{2011A&A...536A..78K} Kishimoto M., H{\"o}nig S.~F., Antonucci R., Millour F., Tristram K.~R.~W., Weigelt G., 2011, A\&A, 536, A78

\bibitem[\protect\citeauthoryear{Riechers et 
al.}{2008}]{2008ApJ...686..851R} Riechers D.~A., Walter F., Brewer B.~J., 
Carilli C.~L., Lewis G.~F., Bertoldi F., Cox P., 2008, ApJ, 686, 851

\bibitem[{{S{\'e}rsic}(1968)}]{Sersic1968}
{S{\'e}rsic}, J.~L. 1968, {Atlas de galaxias australes} (Cordoba, Argentina:
  Observatorio Astronomico)

\bibitem[\protect\citeauthoryear{Sivia \& Skilling}{2006}]{sivia} Sivia, 
D.~ S., Skilling, J., 2006, Data Analysis: A Bayesian Tutorial, 2nd 
Edition, Oxford University Press

\bibitem[\protect\citeauthoryear{Skilling}{2006}]{skilling} Skilling, 
J., 2006, ``Nested Sampling for General Bayesian Computation'', Bayesian 
Analysis 4, pp. 833-860

\bibitem[\protect\citeauthoryear{Suyu et al.}{2006}]{2006MNRAS.371..983S} 
Suyu S.~H., Marshall P.~J., Hobson M.~P., Blandford R.~D., 2006, MNRAS, 
371, 983

\bibitem[\protect\citeauthoryear{Vegetti et 
al.}{2012}]{2012Natur.481..341V} Vegetti S., Lagattuta D.~J., McKean J.~P., 
Auger M.~W., Fassnacht C.~D., Koopmans L.~V.~E., 2012, Natur, 481, 341

\bibitem[\protect\citeauthoryear{Yoon, Weinberg, 
\& Katz}{2011}]{2011MNRAS.414.1625Y} Yoon I., Weinberg M.~D., Katz N., 2011, MNRAS, 414, 1625 
\end{thebibliography}

\end{document}

### 2012-04-16 MakeFigures/joint_marginal.py
Added code for making figures for paper

@@ -1,0 +1,73 @@
+from numpy import *
+from matplotlib.pyplot import *
+import os
+import copy
+import matplotlib
+matplotlib.rcParams['font.size'] = 14
+matplotlib.rcParams['legend.fontsize'] = 14
+
+xmin = -5.0
+xmax =  5.0
+ymin = -5.0
+ymax =  5.0
+n = 101
+
+x = linspace(xmin, xmax, n)
+y = linspace(ymin, ymax, n)
+dy = y[1] - y[0]
+
+[x, y] = meshgrid(x, y)
+y = -y
+
+prior = exp(-0.5*x[0,:]**2)
+prior = prior/trapz(prior, x=x[0,:])
+likelihood = exp(-0.5*(1.5 - x[0,:])**2)
+posterior = prior*likelihood
+posterior = posterior/trapz(posterior, x=x[0,:])
+
+joint_prior = exp(-0.5*x**2)*exp(-0.5*(y-x)**2)
+joint_prior = joint_prior/sum(joint_prior)
+
+joint_posterior = copy.deepcopy(joint_prior)
+which = nonzero(abs(y - 1.5) > 0.5*dy)[0]
+joint_posterior[which] = 0.0
+joint_posterior = joint_posterior/sum(joint_posterior)
+
+figure(1, figsize=(10,10))
+subplots_adjust(left=0.1, right=0.9, bottom=0.1, top=0.9, wspace=0.4, hspace=0.4)
+
+subplot(2,2,1)
+plot(x[0,:], prior, 'b', label='Prior')
+xlim([xmin, xmax])
+ylim([0.0, 0.6])
+xlabel('Parameters $\\theta$')
+ylabel('Probability Density')
+title('Prior (marginal view)')
+
+subplot(2,2,2)
+plot(x[0,:], posterior, 'b', label='Posterior')
+plot(x[0,:], prior, 'r--', label='Prior')
+xlim([xmin, xmax])
+ylim([0.0, 0.6])
+legend(loc='upper left')
+xlabel('Parameters $\\theta$')
+ylabel('Probability Density')
+title('Posterior (marginal view)')
+
+subplot(2,2,3)
+imshow(joint_prior, interpolation='none', extent=(xmin, xmax, ymin, ymax), aspect=1)
+xlabel('Parameters $\\theta$')
+ylabel('Data D')
+title('Prior (joint view)')
+
+subplot(2,2,4)
[…]

### 2012-04-16 MakeFigures/nested.py

@@ -1,0 +1,58 @@
+from numpy import *
+from matplotlib.pyplot import *
+import matplotlib
+matplotlib.rcParams['font.size'] = 14
+matplotlib.rcParams['legend.fontsize'] = 12
+
+x = linspace(-5.0, 5.0, 101)
+L = exp(-0.5*x**2)
+L_alternatives = [L**10, L**0.25, log(L+1.0), 1.0/(1.0 + exp(-L))]
+
+subplot(2,1,1)
+plot(x, L, linewidth=2)
+for l in L_alternatives:
+	plot(x, l/l.max(), '--')
+ylabel('Likelihood')
+xlim([-5.0, 5.0])
+legend(('Formal Model', 'Alternatives'))
+
+subplot(2,1,2)
+p = [ones(x.shape)]
+p[0] = p[0]/trapz(p[0], x=x)
+limits = array([-5.0, 5.0])
+mixture = p[0]
+for i in xrange(0, 5):
+	p_new = p[-1]
+	which = nonzero(logical_or(x < limits[0], x > limits[1]))[0]
+	p_new[which] = 0.0
+	p_new = p_new/trapz(p_new, x=x)
+	mixture = mixture + p_new
+	p.append(p_new)
+	limits = limits*0.5
+
+mixture = mixture/trapz(mixture, x=x)
+plot(x, mixture, 'k')
+
+
+p = [ones(x.shape)]
+p[0] = p[0]/trapz(p[0], x=x)
+limits = array([-5.0, 5.0])
+mixture = p[0]
+for i in xrange(0, 20):
+	p_new = p[-1]
+	which = nonzero(logical_or(x < limits[0], x > limits[1]))[0]
+	p_new[which] = 0.0
+	p_new = p_new/trapz(p_new, x=x)
+	mixture = mixture + p_new
+	p.append(p_new)
+	limits = limits*(10.0/11.0)
+
+mixture = mixture/trapz(mixture, x=x)
+plot(x, mixture, 'b')
+
+xlabel('Parameters $\\theta$')
+ylabel('Probability Density')
+xlim([-5.0, 5.0])
+savefig('nested.eps')
+show()
+

### 2012-04-16 MakeFigures/simple_complex3.py

@@ -1,0 +1,46 @@
+from numpy import *
+from matplotlib.pyplot import *
+from scipy.optimize import fmin
+import matplotlib
+matplotlib.rcParams['font.size'] = 14
+matplotlib.rcParams['legend.fontsize'] = 14
+
+def negative_entropy(params):
+	global x, y, z_complex
+	mu_x = params[0]
+	mu_y = params[1]
+	sig = params[2]
+	z_simple = exp(-0.5*((x - mu_x)**2 + (y - mu_y)**2)/sig**2)
+	z_simple = z_simple/z_simple.sum()
+	return sum(z_complex*log(z_complex/z_simple))
+
+x = linspace(-4.0, 4.0, 101)
+y = linspace(-4.0, 4.0, 101)
+[x, y] = meshgrid(x, y)
+y = -y
+
+component1 = exp(-sqrt(x**2 + ((y+1)/0.5)**2))
+component1 = component1/component1.sum()
+component2 = exp(-0.5*((x - 1.0)**2 + (y - 0.5)**2))
+component2 = component2/component2.sum()
+
+z_complex = 0.5*component1 + 0.5*component2
+
+params = array([0.0, 0.0, 1.0]) # Initial guess for gaussian parameters
+			        # [mu_x, mu_2, sig]
+params = fmin(negative_entropy, params)
+mu_x = params[0]
+mu_y = params[1]
+sig = params[2]
+z_simple = exp(-0.5*((x - mu_x)**2 + (y - mu_y)**2)/sig**2)
+z_simple = z_simple/z_simple.sum()
+
+imshow(z_complex, extent = [-4.0, 4.0, -4.0, 4.0])
+contour(x, y, z_simple, 10, colors="white")
+xlabel('x')
+ylabel('y')
+
+savefig('simple_complex3.eps')
+show()
+
+

### 2012-04-16 MakeFigures/joint_marginal.py
Updated to make prior the same colour on both graphs, and output with tight bounding box

@@ -1,10 +1,9 @@
-from numpy import *
-from matplotlib.pyplot import *
-import os
+from pylab import *
 import copy
-import matplotlib
+
 matplotlib.rcParams['font.size'] = 14
 matplotlib.rcParams['legend.fontsize'] = 14
+#matplotlib.rcParams['lines.linewidth'] = 2
 
 xmin = -5.0
 xmax =  5.0
@@ -37,7 +36,7 @@ figure(1, figsize=(10,10))
 subplots_adjust(left=0.1, right=0.9, bottom=0.1, top=0.9, wspace=0.4, hspace=0.4)
 
 subplot(2,2,1)
-plot(x[0,:], prior, 'b', label='Prior')
+plot(x[0,:], prior, 'r', label='Prior')
 xlim([xmin, xmax])
 ylim([0.0, 0.6])
 xlabel('Parameters $\\theta$')
@@ -45,8 +44,8 @@ ylabel('Probability Density')
 title('Prior (marginal view)')
 
 subplot(2,2,2)
-plot(x[0,:], posterior, 'b', label='Posterior')
-plot(x[0,:], prior, 'r--', label='Prior')
+plot(x[0,:], posterior, 'k', label='Posterior')
+plot(x[0,:], prior, 'r', label='Prior')
 xlim([xmin, xmax])
 ylim([0.0, 0.6])
 legend(loc='upper left')
@@ -55,19 +54,18 @@ ylabel('Probability Density')
 title('Posterior (marginal view)')
 
 subplot(2,2,3)
-imshow(joint_prior, interpolation='none', extent=(xmin, xmax, ymin, ymax), aspect=1)
+imshow(joint_prior, interpolation='nearest', extent=(xmin, xmax, ymin, ymax), aspect=1)
 xlabel('Parameters $\\theta$')
 ylabel('Data D')
 title('Prior (joint view)')
 
 subplot(2,2,4)
-imshow(joint_posterior, interpolation='none', extent=(xmin, xmax, ymin, ymax), aspect=1)
+imshow(joint_posterior, interpolation='nearest', extent=(xmin, xmax, ymin, ymax), aspect=1)
 xlabel('Parameters $\\theta$')
 ylabel('Data D')
 title('Posterior (joint view)')
 
-
-savefig('joint_marginal.eps')
+savefig('joint_marginal.eps', bbox_inches='tight')
 
 show()
 

### 2012-05-16 ms.tex
Added acknowledgement
Added Joey's paper
Random writing

@@
 \documentclass[letterpaper, 11pt]{article}
-\usepackage{graphicx}
-\usepackage{natbib}
+\usepackage{authblk}	% For nice author-affil lists
+\usepackage{graphicx}	% For figures
+\usepackage{natbib}	% For citet and citep
+\usepackage{amsmath}	% for \iint
+\usepackage{bbm}	% for blackboard bold numbers
 \usepackage[left=3cm,top=3cm,right=3cm]{geometry}
@@
 
-\author{%
-  Brendon~J.~Brewer$^{1}$\thanks{\tt brewer@physics.ucsb.edu}, 
-  Geraint~F.~Lewis$^{2}$,
-  Ross Fadely\\
-  \medskip\\
-  $^1$UCSB\\
-  $^2$USyd
+\author[1,2]{Brendon J. Brewer}
+\author[3]{Geraint~F.~Lewis}
+\author[4]{Ross Fadely}
+\affil[1]{\small Dept. of Physics, University of California, Santa Barbara, CA 93106, USA}
+\affil[2]{Department of Statistics, University of Auckland, Private Bag 92019, Auckland, New Zealand
 }
+\affil[3]{Sydney Institute for Astronomy, School of Physics, The University of Sydney, A28, Sydney, 2006, Australia}
+\affil[4]{Department of Astronomy, Haverford College, 370 Lancaster Ave., Haverford, PA 19041 USA}
 
@@
 
-\section{Background on Bayesian Inference}
+\section{Introduction}
 
@@
 
+Bayesian Inference is a powerful framework for modelling uncertainty that has
+been successfully applied in many scientific fields \citep{}. The basic idea
+is that we can model the degree of plausibility of a hypothesis $H$ by a real
+number in $[0, 1]$, and that these numbers should be manipulated according to
+the rules of probability theory. If we are initially uncertain about some
+hypothesis $H$, we model this as a {\it prior probability} $P(H)$. If some other
+hypothesis $D$ is discovered to be true, the plausibility of $H$ is updated to
+the {\it posterior probability} using Bayes' rule:
+\begin{equation}
+P(H|D) = \frac{P(H)P(D|H)}{P(D)}
+\end{equation}
+
+One common application of Bayesian Inference is for parameter estimation.
+Suppose there is some quantity $\theta$ that is unknown. Initially, we describe
+our uncertainty by a prior distribution $p(\theta)$. We also know about some
+observation or experiment that will yield data $D$ that will provide some
+information about $\theta$. We describe our knowledge about this process by 
+{\it sampling distributions} $p(D|\theta)$. Then, once a specific data set
+$D_{\rm obs}$ has been observed, we update our state of knowledge about $\theta$
+to the {\it posterior distribution}:
 \begin{equation}
@@
 
+\bibitem[Richards et al.(2011)]{2011arXiv1105.6344R} Richards, J.~W., Lee, 
+A.~B., Schafer, C.~M., Freeman, P.~E.\ 2011.\ Prototype selection for 
+parameter estimation in complex models.\ ArXiv e-prints arXiv:1105.6344.
+
 \bibitem[\protect\citeauthoryear{Vegetti et 

### 2012-05-16 Code/distribution.py
Simple Gaussian model

@@ -5,71 +5,65 @@ import numpy as np
 import matplotlib.pyplot as plt
 import scipy.optimize
 
-# A Pareto (power-law) distribution
+# A normal distribution
 class Simple:
-	"""
-	Constructor: takes a minimum value cutoff
-	and a slope parameter
-	"""
-	def __init__(self, xMin, alpha):
-		assert xMin > 0 and alpha > 0
-		self.xMin, self.alpha = xMin, alpha
-	"""
-	Evaluate the probability density given a numpy
-	array of x-points
-	"""
-	def pdf(self, x, normalise=False):
-		p = np.zeros(x.shape)
-		good = np.nonzero(x > self.xMin)[0]
-		p[good] = self.alpha*self.xMin**self.alpha/x**(self.alpha + 1)
-		if normalise:
-			p = p/np.trapz(p, x=x)
+	def __init__(self, mu=0., log_sig=0.):
+		"""
+		Constructor: takes a mean and a log-standard deviation
+		"""
+		self.mu, self.sig = mu, np.exp(log_sig)
+
+	def pdf(self, x):
+		"""
+		Evaluate the probability density given a numpy
+		array of x-points
+		"""
+		p = 1./self.sig/np.sqrt(2*np.pi)\
+			*np.exp(-0.5*((x - self.mu)/self.sig)**2)
 		return p
 
-# A mixture of N exponentials
+# A mixture of N concentric gaussians
 class Complex:
-	"""
-	Constructor: takes a numpy array of 
-	means and weights
-	"""
-	def __init__(self, xMin, means, weights):
-		assert weights.size == means.size
-		assert xMin > 0
-		weights = weights/weights.sum()
-		self.xMin, self.means, self.weights = xMin, means, weights
-		
-	def pdf(self, x, normalise=False):
+	def __init__(self, mu=0., sig=np.array([1.,1.]),\
+			weights=np.array([0.5, 0.5])):
+		"""
+		Constructor: takes a mean, a tuple of sigmas
+		and a tuple of not-necessarily normalised weights
+		"""
+		assert sig.size == weights.size
+		assert np.all(weights >= 0.) and np.all(sig > 0.)
+		self.N = sig.size
+		self.mu, self.sig, self.weights = mu, sig, weights/weights.sum()
+
+	def pdf(self, x):
 		p = np.zeros(x.shape)
[…]

### 2012-05-16 Code/distribution.py
Can generate data from Complex

@@ -2,6 +2,7 @@
 Code for fitting a simple 1-D PDF to a complex one, by maximum entropy
 """
 import numpy as np
+import numpy.random as rng
 import matplotlib.pyplot as plt
 import scipy.optimize
 
@@ -42,8 +43,16 @@ class Complex:
 				*np.exp(-0.5*((x - self.mu)/self.sig[i])**2)
 		return p
 
-	def generate_data(self):
-		pass
+	def generate_data(self, num=10):
+		data = np.empty(num)
+		max_weight = self.weights.max()
+		for i in xrange(0, num):
+			# Choose a component
+			which = rng.randint(self.N)
+			while rng.rand() >= self.weights[which]/max_weight:
+				which = rng.randint(self.N)
+			data[i] = self.mu + self.sig[which]*rng.randn()
+		return data
 
 def utility(simple, complicated, x):
 	U = np.trapz(complicated.pdf(x)*np.log(simple.pdf(x) + 1E-300), x=x)
@@ -51,7 +60,7 @@ def utility(simple, complicated, x):
 
 # Executable code
 if __name__ == '__main__':
-	x = np.linspace(-10., 10., 1001)
+	x = np.linspace(-30., 30., 10001)
 	complicated = Complex(mu=0., sig=np.array([0.3, 1., 3.]),\
 				weights=np.array([0.5, 0.5, 0.5]))
 

### 2012-08-07 ms.tex
Small tweaks

@@
 
-\title{Robust Inferences from Simply Parameterised Models}
+\title{Reliable Inferences from Simply Parameterised Models}
 
@@
 \item $p(D|\theta)$ is a function of
-both $\theta$ and $D$ and is referred to as the {\it sampling distributions}. 
-The reason for the awkward plural is that $p(D|\theta)$ is a set of probability distributions,
-one for each value of $\theta$. The sampling distributions describe our prior information about how the data are connected to the parameters \citep{2008arXiv0808.0012C}. \\
+both $\theta$ and $D$ and is referred to as the {\it sampling distribution}. 
+The sampling distribution $p(D|\theta)$ is a set of probability distributions,
+one for each value of $\theta$, and describe our prior information about how the data are connected to the parameters \citep{2008arXiv0808.0012C}.
 
 \item $p(D|\theta)|_{D = D_{\rm obs}}$ is called the {\it likelihood function}.
-It is obtained from the sampling distributions, with the actual data substituted in,
+It is obtained from the sampling distribution, with the actual data substituted in,
 and is therefore a function of $\theta$ only. It describes the effects of the actual data
@@
 
-\section{Advantages and Disadvantages of Simply Parameterised Models}
+\section{The Failure of Simply Parameterised Models}
 \begin{itemize}
@@
 \section*{Acknowledgements}
-Tommaso Treu, Anna Pancoast, Phil Marshall, Matthew Auger, Greg Dobler, Sebastian Hoenig
+Tommaso Treu, Anna Pancoast, Phil Marshall, Matthew Auger, Greg Dobler, Sebastian Hoenig, Douglas Applegate
 

### 2012-08-08 ms.tex
MCMC para

@@
 In principle, the best solution to this problem is to develop more realistic complex models that accurately describe our prior beliefs.
-However, this is often infeasible in practice, due to computational limitations and the difficulty of defining realistic prior distributions over high dimensional spaces.
+However, this is often infeasible in practice, due to computational limitations and the difficulty of defining satisfactory prior distributions over high dimensional spaces.
 As a pragmatic alternative, we show that it is possible to reinterpret the use of simple models in a way that avoids the problem of overconfident
@@
 \end{figure*}
+
+When the number of parameters being inferred is 3 or greater, enumeration of
+all possible values becomes computationally prohibitive. In this situation,
+Markov Chain Monte Carlo (MCMC) methods are commonly used to produce samples
+drawn from the posterior distribution. These samples can then be used to view
+the marginal distribution for any particular parameter(s) of interest. If the
+samples are viewed as a movie, they can give the viewer an intuitive sense of
+the uncertainty in the determination of the parameters: any feature of the
+models that varies between frames is a conclusion that is uncertain, and any
+feature that is common to all models in the sample is a feature that has a high
+posterior probability.
 

### 2012-08-08 ms.tex
Simple vs complex sections

@@
 drawn from the posterior distribution. These samples can then be used to view
-the marginal distribution for any particular parameter(s) of interest. If the
+the marginal distribution for any particular parameter(s) of interest.
+In addition, if the
 samples are viewed as a movie, they can give the viewer an intuitive sense of
 the uncertainty in the determination of the parameters: any feature of the
-models that varies between frames is a conclusion that is uncertain, and any
-feature that is common to all models in the sample is a feature that has a high
+models that varies between movie frames is a conclusion that is uncertain, and any
+feature that is common to all frames in the movie is a feature that has a high
 posterior probability.
+
+\section{Two Kinds of Model}
+In this paper we consider two general categories of models that can be fit to
+data. The first of these we will call ``simply-parameterised'' models.
+
+\subsection{Simply-Parameterised Models}
+Simply-parameterised models, which are also
+commonly known as parametric models, are in widespread use for a number of reasons.
+Firstly, they are easy to implement in software, and sometimes analytical
+solutions are available for the inference of their parameters from data.
+Secondly, their parameters usually have simple meanings that are easy to interpret.
+This property makes communication easy, as well as making it straightforward to
+make uncontroversial prior probability
+assignments to the possible values of the parameters. Finally, when the inference
+is done computationally, the MCMC methods tend to work very well.
+
+\subsection{Complex Models}
+The second category of models we consider are ``complex'' models. These tend to
+be much more flexible and contain large numbers of unknown parameters. Complex
+models are often incorrectly referred to as nonparametric models. A better term
+would be flexible models or free-form models.
+
+The primary advantage of complex models is realism. The universe is not
+simple place, and it is rare that a physical situation can be described accurately
+by a simply-parameterised model which is often a single mathematical equation.
+
+\section{Example: Fitting an Emission Line}
+Throughout this paper we will use a simple example of fitting an emission line
+to noisy data in order to estimate the total flux of the line.
 

### 2012-08-08 ms.tex
Words

@@
 
-\section{Example: Fitting an Emission Line}
+\section{Example 2: Fitting an Emission Line}
 Throughout this paper we will use a simple example of fitting an emission line
 to noisy data in order to estimate the total flux of the line.
+
+\subsection{The Simply-Parameterised Model}
+The model for the shape of the line is:
+\begin{eqnarray}
+\mathcal{M}(x; a, b, c) &=& \exp\left[\right]
+\end{eqnarray}
+
+\subsection{The Sampling Distribution}
+The sampling distribution, aka the probability distribution for the data given
+the parameters, is simply a multivariate normal distribution. Note that the
+gaussian error assumption should be distinguished from the assumption of a gaussian
+shape for the emission line.
+
+\begin{eqnarray}
+p(\mathbf{y}|a, b, c) &=& \prod_{i=1}^N
+\frac{1}{\sigma\sqrt{2\pi}}
+\exp
+\left[
+-\frac{1}{2\sigma^2}\left(y_i - \mathcal{M}(x_i; a, b, c)\right)^2
+\right]
+\end{eqnarray}
 

### 2012-08-08 ms.tex
SOmething or other

--- 2012-08-08 ms.tex
@@
 \parindent=0cm
+\newcommand{\yy}{\mathbf{y}}
 
@@
 
-\section{Example: Fitting an Emission Line}
+\section{Example 1: Fitting an Emission Line}
 Throughout this paper we will use a simple example of fitting an emission line
 to noisy data in order to estimate the total flux of the line.
+
+\subsection{The Simply-Parameterised Model}
+The model for the shape of the line is:
+\begin{eqnarray}
+\mathcal{M}(x; A, c, w) &=&
+A\exp
+\left[
+-\frac{1}{2w^2}
+\left(x - c\right)^2
+\right]
+\end{eqnarray}
+where $A$ is the peak amplitude, $c$ is the central position of the line
+and $w$ is the line width. To infer the parameters $\{A, c, w\}$ from some data
+$\yy$, we will use Bayes' rule:
+\begin{eqnarray}
+p(A, c, w | \yy) \propto p(A, c, w)p(\yy | A, c, w).
+\end{eqnarray}
+To proceed, we just need to define the prior and the sampling distribution.
+
+\subsection{The Sampling Distribution}
+We will assume that the data are simply noisy measurements of the true line shape
+$\mathcal{M}(x)$ at a finite number of $x$-values.
+The sampling distribution, aka the probability distribution for the data $\yy$ given
+the parameters, is simply a normal/gaussian distribution. Note that the
+gaussian error assumption should be distinguished from the assumption of a gaussian
+shape for the emission line.
+
+\begin{eqnarray}
+p(\yy|A, c, w) &=& \prod_{i=1}^N
+\frac{1}{\sigma\sqrt{2\pi}}
+\exp
+\left[
+-\frac{1}{2\sigma^2}\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2
+\right].
+\end{eqnarray}
 

### 2012-08-09 MakeFigures/emission_line.py
Generate simulated emission line and plot it

@@ -1,0 +1,5 @@
+from pylab import *
+
+x = linspace(-20., 20., 1.)
+
+

### 2012-08-09 MakeFigures/emission_line.py
Makes emission line

@@ -1,5 +1,20 @@
 from pylab import *
 
-x = linspace(-20., 20., 1.)
+x = linspace(-20., 20., 41)
 
+# Noise-free data (i.e. model curve)
+M = exp(-0.5*x**2) + 1./2*exp(-0.5*(x/2)**2) + exp(-0.5*(x - 2.7)**2)
+M = M/M.sum()
+
+# Noisy data
+sig = 0.03
+y = M + sig*randn(M.size)
+
+plot(x, M, 'ko-', linewidth=2)
+errorbar(x, y, yerr=sig*ones(y.size), fmt='bo')
+
+ylim([-0.05*y.max(), 1.05*y.max()])
+xlabel('Wavelength $\\lambda$', fontsize=14)
+ylabel('Flux', fontsize=14)
+show()
 

### 2012-08-15 MakeFigures/emission_line.py
Emission line simulated data and figure

@@ -1,0 +1,30 @@
+from pylab import *
+
+figure(figsize=(8, 12))
+seed(0)
+x = linspace(-10., 10., 101)
+
+M = exp(-0.5*(x/0.3)**2) + exp(-0.5*(x-1.)**2)
+M = M/sum(M)
+sig = 0.003*ones(M.shape)
+y = M + sig*randn(M.size)
+
+subplot(2,1,1)
+plot(x, M, 'k.-', markersize=10)
+xlabel('$x$', fontsize=24)
+ylabel('Flux', fontsize=16)
+plot([-10., 10.], [0., 0.], 'b')
+ylim([-0.03, 0.13])
+title('True Noise-Free Curve')
+
+subplot(2,1,2)
+errorbar(x, y, yerr=sig, fmt='ro', markersize=3)
+xlabel('$x$', fontsize=24)
+ylabel('Flux', fontsize=16)
+plot([-10., 10.], [0., 0.], 'b')
+ylim([-0.03, 0.13])
+title('Noisy Data')
+
+savefig('../emission_line.eps')
+show()
+

### 2012-08-15 Code/distribution.py
Removal

@@ -1,78 +1,0 @@
-"""
-Code for fitting a simple 1-D PDF to a complex one, by maximum entropy
-"""
-import numpy as np
-import numpy.random as rng
-import matplotlib.pyplot as plt
-import scipy.optimize
-
-# A normal distribution
-class Simple:
-	def __init__(self, mu=0., log_sig=0.):
-		"""
-		Constructor: takes a mean and a log-standard deviation
-		"""
-		self.mu, self.sig = mu, np.exp(log_sig)
-
-	def pdf(self, x):
-		"""
-		Evaluate the probability density given a numpy
-		array of x-points
-		"""
-		p = 1./self.sig/np.sqrt(2*np.pi)\
-			*np.exp(-0.5*((x - self.mu)/self.sig)**2)
-		return p
-
-# A mixture of N concentric gaussians
-class Complex:
-	def __init__(self, mu=0., sig=np.array([1.,1.]),\
-			weights=np.array([0.5, 0.5])):
-		"""
-		Constructor: takes a mean, a tuple of sigmas
-		and a tuple of not-necessarily normalised weights
-		"""
-		assert sig.size == weights.size
-		assert np.all(weights >= 0.) and np.all(sig > 0.)
-		self.N = sig.size
-		self.mu, self.sig, self.weights = mu, sig, weights/weights.sum()
-
-	def pdf(self, x):
-		p = np.zeros(x.shape)
-		for i in xrange(0, self.N):
-			p += self.weights[i]/self.sig[i]/np.sqrt(2*np.pi)\
-				*np.exp(-0.5*((x - self.mu)/self.sig[i])**2)
-		return p
-
-	def generate_data(self, num=10):
-		data = np.empty(num)
-		max_weight = self.weights.max()
-		for i in xrange(0, num):
-			# Choose a component
-			which = rng.randint(self.N)
-			while rng.rand() >= self.weights[which]/max_weight:
-				which = rng.randint(self.N)
-			data[i] = self.mu + self.sig[which]*rng.randn()
-		return data
-
-def utility(simple, complicated, x):
-	U = np.trapz(complicated.pdf(x)*np.log(simple.pdf(x) + 1E-300), x=x)
-	return U
-
-# Executable code
-if __name__ == '__main__':
-	x = np.linspace(-30., 30., 10001)
-	complicated = Complex(mu=0., sig=np.array([0.3, 1., 3.]),\
[…]

### 2012-08-15 MakeFigures/emission_line.py
Save sim data

@@ -26,5 +26,10 @@ ylim([-0.03, 0.13])
 title('Noisy Data')
 
 savefig('../emission_line.eps')
+data = empty((x.size, 3))
+data[:,0] = x
+data[:,1] = y
+data[:,2] = sig
+savetxt('../Code/emission_line_data.txt', data)
 show()
 

### 2012-08-15 Code/Emission_Line/Data.h
Emission line fitting

@@ -1,0 +1,63 @@
+/*
+* Copyright (c) 2009, 2010, 2011, 2012 Brendon J. Brewer.
+*
+* This file is part of DNest3.
+*
+* DNest3 is free software: you can redistribute it and/or modify
+* it under the terms of the GNU General Public License as published by
+* the Free Software Foundation, either version 3 of the License, or
+* (at your option) any later version.
+*
+* DNest3 is distributed in the hope that it will be useful,
+* but WITHOUT ANY WARRANTY; without even the implied warranty of
+* MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+* GNU General Public License for more details.
+*
+* You should have received a copy of the GNU General Public License
+* along with DNest3. If not, see <http://www.gnu.org/licenses/>.
+*/
+
+#ifndef _Data_
+#define _Data_
+
+#include <vector>
+
+/*
+* A dataset
+* Also contains a static singleton for the one-data-set case
+*/
+
+class Data
+{
+	private:
+		// A flag
+		bool loaded;
+
+		// The data
+		std::vector<double> x, y, sig;
+
+	public:
+		// Default constructor: Empty data
+		Data();
+
+		// Load the data from file
+		void load(const char* filename);
+
+		// Getters
+		bool get_loaded() { return loaded; }
+		double get_x(int i) { return x[i]; }
+		double get_y(int i) { return y[i]; }
+		double get_sig(int i) { return sig[i]; }
+		int get_N() { return static_cast<int>(y.size()); }
+
+	// Static stuff for singleton use
+	private:
+		static Data instance;
+
+	public:
+		// Access to the instance
+		static Data& get_instance() { return instance; }
+};
+
+#endif
+

### 2012-08-15 Code/Emission_Line/FitLine.cpp

@@ -1,0 +1,94 @@
+/*
+* Copyright (c) 2009, 2010, 2011, 2012 Brendon J. Brewer.
+*
+* This file is part of DNest3.
+*
+* DNest3 is free software: you can redistribute it and/or modify
+* it under the terms of the GNU General Public License as published by
+* the Free Software Foundation, either version 3 of the License, or
+* (at your option) any later version.
+*
+* DNest3 is distributed in the hope that it will be useful,
+* but WITHOUT ANY WARRANTY; without even the implied warranty of
+* MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+* GNU General Public License for more details.
+*
+* You should have received a copy of the GNU General Public License
+* along with DNest3. If not, see <http://www.gnu.org/licenses/>.
+*/
+
+#include "FitLine.h"
+#include "RandomNumberGenerator.h"
+#include "Utils.h"
+#include "Data.h"
+#include <cmath>
+#include <iostream>
+
+using namespace std;
+using namespace DNest3;
+
+FitLine::FitLine()
+{
+
+}
+
+void FitLine::fromPrior()
+{
+	A = exp(log(1E-3) + log(1E6)*randomU());
+	c = -10. + 20.*randomU();
+	w = exp(log(1E-3) + log(1E6)*randomU());
+}
+
+double FitLine::perturb()
+{
+	double logH = 0.;
+	
+	if(randomU() <= 0.33333)
+	{
+		A = log(A);
+		A += log(1E6)*pow(10., 1.5 - 6*randomU())*randn();
+		A = mod(A - log(1E-3), log(1E6)) + log(1E-3);
+		A = exp(A);
+	}
+	else if(randomU() <= 0.5)
+	{
+		c += 20*pow(10., 1.5 - 6*randomU())*randn();
+		c = mod(c + 10., 20.) - 10.;
+	}
+	else
+	{
+		w = log(w);
+		w += log(1E6)*pow(10., 1.5 - 6*randomU())*randn();
+		w = mod(w - log(1E-3), log(1E6)) + log(1E-3);
+		w = exp(w);
+	}
+
+	return logH;
+}
+
+double FitLine::logLikelihood() const
+{
+	double mock;
+	double chisq = 0.;
+	for(int i=0; i<Data::get_instance().get_N(); i++)
+	{
[…]

### 2012-08-15 Code/Emission_Line/FitLine.h

@@ -1,0 +1,52 @@
+/*
+* Copyright (c) 2009, 2010, 2011, 2012 Brendon J. Brewer.
+*
+* This file is part of DNest3.
+*
+* DNest3 is free software: you can redistribute it and/or modify
+* it under the terms of the GNU General Public License as published by
+* the Free Software Foundation, either version 3 of the License, or
+* (at your option) any later version.
+*
+* DNest3 is distributed in the hope that it will be useful,
+* but WITHOUT ANY WARRANTY; without even the implied warranty of
+* MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+* GNU General Public License for more details.
+*
+* You should have received a copy of the GNU General Public License
+* along with DNest3. If not, see <http://www.gnu.org/licenses/>.
+*/
+
+#ifndef _FitLine_
+#define _FitLine_
+
+#include "Model.h"
+#include <vector>
+
+class FitLine:public DNest3::Model
+{
+	private:
+		double A, c, w;		
+
+	public:
+		FitLine();
+
+		// Generate the point from the prior
+		void fromPrior();
+
+		// Metropolis-Hastings proposals
+		double perturb();
+
+		// Likelihood function
+		double logLikelihood() const;
+
+		// Print to stream
+		void print(std::ostream& out) const;
+
+		// Return string with column information
+		std::string description() const;
+
+};
+
+#endif
+

### 2012-08-15 Code/Emission_Line/display.py

@@ -1,0 +1,27 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+data = np.loadtxt('../emission_line_data.txt')
+x = data[:,0]
+sample = np.atleast_2d(np.loadtxt('posterior_sample.txt'))
+
+plt.ion()
+
+flux = np.empty(sample.shape[0])
+for i in xrange(0, sample.shape[0]):
+	mock = sample[i, 0]*np.exp(-0.5*((x - sample[i, 1])/sample[i, 2])**2)
+	flux[i] = sum(mock)
+
+	plt.hold(False)
+	plt.plot(x, mock, 'k')
+	plt.hold(True)
+	plt.errorbar(x, data[:,1], yerr=data[:,2], fmt='ro')
+	plt.title(str(i+1))
+	plt.draw()
+
+plt.ioff()
+plt.show()
+
+plt.hist(flux, 30)
+plt.show()
+

### 2012-08-15 Code/Emission_Line/main.cpp

@@ -1,0 +1,50 @@
+/*
+* Copyright (c) 2009, 2010, 2011, 2012 Brendon J. Brewer.
+*
+* This file is part of DNest3.
+*
+* DNest3 is free software: you can redistribute it and/or modify
+* it under the terms of the GNU General Public License as published by
+* the Free Software Foundation, either version 3 of the License, or
+* (at your option) any later version.
+*
+* DNest3 is distributed in the hope that it will be useful,
+* but WITHOUT ANY WARRANTY; without even the implied warranty of
+* MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+* GNU General Public License for more details.
+*
+* You should have received a copy of the GNU General Public License
+* along with DNest3. If not, see <http://www.gnu.org/licenses/>.
+*/
+
+#include <iostream>
+#include "Start.h"
+#include "Data.h"
+#include "FitLine.h"
+
+using namespace std;
+using namespace DNest3;
+
+int main(int argc, char** argv)
+{
+	// Process command line options and load data
+	CommandLineOptions options(argc, argv);
+	string dataFile = options.get_dataFile();
+	if(dataFile.compare("") == 0)
+		Data::get_instance().load("../emission_line_data.txt");
+	else
+		Data::get_instance().load(dataFile.c_str());
+
+	// Initialise the sampler
+	#ifndef DNest3_No_Boost
+	MTSampler<FitLine> sampler = setup_mt<FitLine>(options);
+	#else
+	Sampler<FitLine> sampler = setup<FitLine>(options);
+	#endif
+
+	// Go!
+	sampler.run();
+
+	return 0;
+}
+

### 2012-08-15 Code/Emission_Line/showresults.py

@@ -1,0 +1,22 @@
+# Copyright (c) 2009, 2010, 2011, 2012 Brendon J. Brewer.
+#
+# This file is part of DNest3.
+#
+# DNest3 is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# DNest3 is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with DNest3. If not, see <http://www.gnu.org/licenses/>.
+
+# Import postprocess from two directories up
+# http://stackoverflow.com/a/9806045
+import postprocess
+postprocess.postprocess()
+import display

### 2012-08-15 MakeFigures/emission_line.py
New fake data -- more dramatic failure

@@ -4,7 +4,7 @@ figure(figsize=(8, 12))
 seed(0)
 x = linspace(-10., 10., 101)
 
-M = exp(-0.5*(x/0.3)**2) + exp(-0.5*(x-1.)**2)
+M = 2*exp(-0.5*(x/0.3)**2) + exp(-0.5*(x-1.)**2)
 M = M/sum(M)
 sig = 0.003*ones(M.shape)
 y = M + sig*randn(M.size)

### 2012-08-17 Code/Emission_Line/FitLine.cpp
sigmaBoost still doesn't save us!

@@ -37,30 +37,40 @@ void FitLine::fromPrior()
 	A = exp(log(1E-3) + log(1E6)*randomU());
 	c = -10. + 20.*randomU();
 	w = exp(log(1E-3) + log(1E6)*randomU());
+	sigmaBoost = exp(3*randn());
 }
 
 double FitLine::perturb()
 {
 	double logH = 0.;
 	
-	if(randomU() <= 0.33333)
+	int which = randInt(4);
+	if(which == 0)
 	{
 		A = log(A);
 		A += log(1E6)*pow(10., 1.5 - 6*randomU())*randn();
 		A = mod(A - log(1E-3), log(1E6)) + log(1E-3);
 		A = exp(A);
 	}
-	else if(randomU() <= 0.5)
+	else if(which == 1)
 	{
 		c += 20*pow(10., 1.5 - 6*randomU())*randn();
 		c = mod(c + 10., 20.) - 10.;
 	}
-	else
+	else if(which == 2)
 	{
 		w = log(w);
 		w += log(1E6)*pow(10., 1.5 - 6*randomU())*randn();
 		w = mod(w - log(1E-3), log(1E6)) + log(1E-3);
 		w = exp(w);
+	}
+	else
+	{
+		sigmaBoost = log(sigmaBoost);
+		logH -= -0.5*pow(sigmaBoost/3., 2);
+		sigmaBoost += 3.*pow(10., 1.5 - 6.*randomU())*randn();
+		logH += -0.5*pow(sigmaBoost/3., 2);
+		sigmaBoost = exp(sigmaBoost);
 	}
 
 	return logH;
@@ -68,26 +78,29 @@ double FitLine::perturb()
 
 double FitLine::logLikelihood() const
 {
-	double mock;
-	double chisq = 0.;
+	double mock, sig;
+	double logL = 0.;
 	for(int i=0; i<Data::get_instance().get_N(); i++)
 	{
 		mock = A*exp(-0.5*pow((Data::get_instance().get_x(i) - c)/w, 2));
-		chisq += pow((Data::get_instance().get_y(i) - mock)/Data::get_instance().get_sig(i), 2);
+		sig = sigmaBoost*Data::get_instance().get_sig(i);
+
+		logL += -log(sig);
+		logL += -0.5*pow((Data::get_instance().get_y(i) - mock)/sig, 2);
 	}
 
-	return -0.5*chisq;
+	return logL;
 }
 
 
[…]

### 2012-08-17 Code/Emission_Line/FitLine.h

@@ -26,7 +26,8 @@
 class FitLine:public DNest3::Model
 {
 	private:
-		double A, c, w;		
+		double A, c, w;
+		double sigmaBoost;		
 
 	public:
 		FitLine();

### 2012-08-17 Code/Emission_Line/FitLine.cpp
More extreme data -- more dramatic faulure

@@ -37,7 +37,7 @@ void FitLine::fromPrior()
 	A = exp(log(1E-3) + log(1E6)*randomU());
 	c = -10. + 20.*randomU();
 	w = exp(log(1E-3) + log(1E6)*randomU());
-	sigmaBoost = exp(3*randn());
+	sigmaBoost = exp(5*randn());
 }
 
 double FitLine::perturb()
@@ -67,9 +67,9 @@ double FitLine::perturb()
 	else
 	{
 		sigmaBoost = log(sigmaBoost);
-		logH -= -0.5*pow(sigmaBoost/3., 2);
-		sigmaBoost += 3.*pow(10., 1.5 - 6.*randomU())*randn();
-		logH += -0.5*pow(sigmaBoost/3., 2);
+		logH -= -0.5*pow(sigmaBoost/5., 2);
+		sigmaBoost += 5.*pow(10., 1.5 - 6.*randomU())*randn();
+		logH += -0.5*pow(sigmaBoost/5., 2);
 		sigmaBoost = exp(sigmaBoost);
 	}
 

### 2012-08-17 MakeFigures/emission_line.py

@@ -4,7 +4,7 @@ figure(figsize=(8, 12))
 seed(0)
 x = linspace(-10., 10., 101)
 
-M = 2*exp(-0.5*(x/0.3)**2) + exp(-0.5*(x-1.)**2)
+M = 3*exp(-0.5*(x/0.3)**2) + exp(-0.5*(x-1.)**2) + 5*exp(-0.5*((x+1)/0.5)**2)
 M = M/sum(M)
 sig = 0.003*ones(M.shape)
 y = M + sig*randn(M.size)

### 2012-08-17 MakeFigures/emission_line.py
OK, more extreme

@@ -2,11 +2,11 @@ from pylab import *
 
 figure(figsize=(8, 12))
 seed(0)
-x = linspace(-10., 10., 101)
+x = linspace(-10., 10., 1001)
 
 M = 3*exp(-0.5*(x/0.3)**2) + exp(-0.5*(x-1.)**2) + 5*exp(-0.5*((x+1)/0.5)**2)
 M = M/sum(M)
-sig = 0.003*ones(M.shape)
+sig = 0.0003*ones(M.shape)
 y = M + sig*randn(M.size)
 
 subplot(2,1,1)

### 2012-08-18 Code/Emission_Line/display.py
Gaussian approximation to posterior

@@ -23,5 +23,6 @@ plt.ioff()
 plt.show()
 
 plt.hist(flux, 30)
+print((flux.mean(), flux.std(), (flux.mean() - 1.)/flux.std()))
 plt.show()
 

### 2012-08-29 ms.tex
Chi squared
Emission line figure
Editing of intro

@@
 
-\begin{itemize}
-\item Define terminology very carefully, present Bayes' rule \\
-\item Describe the ``joint'' (parameters $\times$ data space) view of inference, describe how the form of the likelihood function is prior information \citep{caticha} \\
-\item Discuss use of MCMC techniques for complex problems \\
-\item Discuss the various attempts at robustness/model checking/elicitation and that stuff
-\end{itemize}
-
 Bayesian Inference is a powerful framework for modelling uncertainty that has
-been successfully applied in many scientific fields \citep{}. The basic idea
+been successfully applied in many scientific fields. The basic idea
 is that we can model the degree of plausibility of a hypothesis $H$ by a real
@@
 Suppose there is some quantity $\theta$ that is unknown. Initially, we describe
-our uncertainty by a prior distribution $p(\theta)$. We also know about some
+our uncertainty by a prior probability distribution $p(\theta)$. We also know about some
 observation or experiment that will yield data $D$ that will provide some
-information about $\theta$. We describe our knowledge about this process by 
-{\it sampling distributions} $p(D|\theta)$. Then, once a specific data set
+information about $\theta$. We describe our knowledge about this process by a 
+set of conditional probability distributions $p(D|\theta)$. Then, once a specific data set
 $D_{\rm obs}$ has been observed, we update our state of knowledge about $\theta$
@@
 over possible values for $\theta$ that describes our uncertainty about
-$\theta$ before taking into account the data. Commonly, this is a broad
-probability distribution, describing a large amount of uncertainty. \\
+$\theta$ before taking into account the data. In many applications, this is a broad
+probability distribution describing a large amount of uncertainty. \\
 
 \item $p(D|\theta)$ is a function of
-both $\theta$ and $D$ and is referred to as the {\it sampling distribution}. 
+both $\theta$ and $D$ and is sometimes referred to as the {\it sampling distribution}.
+Another name is the generative model. 
 The sampling distribution $p(D|\theta)$ is a set of probability distributions,
-one for each value of $\theta$, and describe our prior information about how the data are connected to the parameters \citep{2008arXiv0808.0012C}.
+one for each value of $\theta$, and describe our prior information about how the data are connected to the parameters \citep{2008arXiv0808.0012C}. In particular, it is the probability distribution
+for the data we might observe, {\it if} we knew the true value of the parameters
+$\theta$, as a function of $\theta$.
 
@@
 posterior probability.
+
+{\bf Discuss the various attempts at robustness/model checking/elicitation and that stuff}
 
@@
 -\frac{1}{2\sigma^2}\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2
-\right].
+\right] \\
+&\propto& \exp\left[-\frac{1}{2\sigma^2}\sum_{i=1}^N\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2\right] \\
+&\propto& \exp\left[-\frac{1}{2}\chi^2\right].
 \end{eqnarray}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.5]{emission_line.eps}
+\end{center}
+\end{figure*}
 

### 2012-08-29 ms.tex
The formula for the simulated data

@@
 models are often incorrectly referred to as nonparametric models. A better term
-would be flexible models or free-form models.
+would be flexible models or free-form models. The primary advantage of complex models is realism. The universe is not
+simple place, and it is rare that a physical situation can be described accurately
+by a simply-parameterised model which is often a simple mathematical formula.
 
-The primary advantage of complex models is realism. The universe is not
-simple place, and it is rare that a physical situation can be described accurately
-by a simply-parameterised model which is often a single mathematical equation.
-
-\section{Example 1: Fitting an Emission Line}
+\section{An Example: Fitting an Emission Line}
 Throughout this paper we will use a simple example of fitting an emission line
-to noisy data in order to estimate the total flux of the line.
+to noisy data to explore the properties of simply parameterised models. The
+simulated data was generated from the following complex model:
+\begin{eqnarray}
+\mathcal{M}_0(x) \propto 3\exp\left[-\frac{1}{2}\left(\frac{x}{0.3}\right)^2\right]
++ \exp\left[-\frac{1}{2}\left(\frac{x - 1}{1}\right)^2\right]
++ 5\exp\left[-\frac{1}{2}\left(\frac{x + 1}{0.5}\right)^2\right]
+%M = 3*exp(-0.5*(x/0.3)**2) + exp(-0.5*(x-1.)**2) + 5*exp(-0.5*((x+1)/0.5)**2)
+\end{eqnarray}
+The fluxes were evaluated at $x$-values ranging from $-10$ to $10$ in steps
+of $0.001$, and then normalised to sum to 1:
+\begin{eqnarray}
+\sum_{i=1}^N \mathcal{M}_0(x_i) &=& 1.
+\end{eqnarray}
 

### 2012-08-29 ms.tex
Adding noise
Fake data figure

@@
 \end{eqnarray}
+To simulate noise in the measurement process, errors $\{\epsilon_i\}$ were added, generated
+independently from a normal distribution with mean 0 and standard deviation
+$\sigma = 3 \times 10^{-4}$.
+This produces noisy data $\mathbf{y} = \{y_1, y_2, ..., y_N\}$:
+\begin{eqnarray}
+\begin{array}{lccr}
+y_i = \mathcal{M}_0(x_i) + \epsilon_i, & & & \epsilon_i \sim \mathcal{N}(0, \sigma^2).
+\end{array}
+\end{eqnarray}
+The simulated data is shown in Figure~\ref{emission_line}.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.5]{emission_line.eps}
+\end{center}
+\caption{The simulated data that will be used to illustrate the properties of
+simply-parameterised models. {\bf Top}: The noise-free true model $\mathcal{M}_0(x)$,
+generated from a mixture of three Gaussians, and normalised to a sum of 1.
+{\bf Bottom}: Simulated data with added noise.\label{emission_line}}
+\end{figure*}
 
@@
 \end{eqnarray}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=0.5]{emission_line.eps}
-\end{center}
-\end{figure*}
 

### 2012-08-29 ms.tex
Priors

@@
 
-\subsection{The Simply-Parameterised Model}
+\section{Fitting a Simply-Parameterised Model}
+We now explore what happens when we fit simulated data (bottom panel of
+Figure~\ref{emission_line}) with an inflexible simply-parameterised model.
+We will fit the data with single Gaussian component.
 The model for the shape of the line is:
@@
 and $w$ is the line width. To infer the parameters $\{A, c, w\}$ from some data
-$\yy$, we will use Bayes' rule:
+$\yy = \{y_1, y_2, ..., y_N\}$, we will use Bayes' rule:
 \begin{eqnarray}
@@
 &\propto& \exp\left[-\frac{1}{2\sigma^2}\sum_{i=1}^N\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2\right] \\
-&\propto& \exp\left[-\frac{1}{2}\chi^2\right].
+&\propto& \exp\left[-\frac{1}{2}\chi^2({\tt model}, {\tt data})\right].
 \end{eqnarray}
+The likelihood here is related to the commonly used $\chi^2$ deviation between
+te model and the data.
+
+\subsection{The Prior Distribution}
+To proceed with the inference, we require a prior distribution over the space
+of possible parameter values for $A$, $c$ and $w$. We shall assume independence:
+\begin{eqnarray}
+p(A, c, w) = p(A)p(c)p(w).
+\end{eqnarray}
+This means that, prior to learning the data, we are unaware of any logical
+connection between the values of the parameters. In other words, if we learned the
+value of any parameter we would not update our knowledge about the others.
+For the central position $c$ of the line, we assigned a uniform prior between
+$-10$ and $10$, which is the same range as the data. For $A$ and $w$ we assigned
+priors proportional to $1/A$ and $1/w$ between $10^{-3}$ and $10^{+3}$, since these
+parameters are known to be positive and have an uncertain magnitude.
 

### 2012-08-29 ms.tex
More writing on sigma boost etc

@@
 
-\section{The Failure of Simply Parameterised Models}
+\subsection{The Failure of the Simply Parameterised Model}
+We ran the simply parameterised model on the simulated data using the Diffusive
+Nested Sampling algorithm \citep{dnest}
+\footnote{A C++ implementation of Diffusive Nested Sampling is available
+online at {\tt http://github.com/eggplantbren/DNest3/}.}. This provides samples
+from the posterior distribution for the parameters $A$, $c$ and $w$. Since these
+parameters do not ``exist'' in reality (i.e. the data were generated from the
+complex model), it does not make much sense to look at the posterior distribution
+for the parameters. However, consider the total flux:
+\begin{eqnarray}
+F = \sum_{i=1}^N \mathcal{M}(x_i)
+\end{eqnarray}
+This can be computed both for the true underlying complex model, and the fitted
+simple models. In other words, it ``exists''. We computed the posterior distribution
+for the total flux using the posterior samples. These are plotted in
+Figure~\ref{failure}.
+
+A commonly suggested technique \citep[e.g.][]{gregory} to avoid this situation
+is to add an ``error-bar boost'' parameter which we will call $\kappa$.
+This adds one more parameter to the list, and the likelihood becomes:
+\begin{eqnarray}
+p(\yy|A, c, w, \kappa) &=& \prod_{i=1}^N
+\frac{1}{(\kappa\sigma)\sqrt{2\pi}}
+\exp
+\left[
+-\frac{1}{2(\kappa\sigma)^2}\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2
+\right] \\
+&\propto& \kappa^{-N}\exp\left[-\frac{1}{2(\kappa\sigma)^2}\sum_{i=1}^N\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2\right]
+\end{eqnarray}
+
 \begin{itemize}
@@
 \end{itemize}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=0.25]{simple_complex1.eps}
-\includegraphics[scale=0.25]{simple_complex2.eps}
-\includegraphics[scale=0.25]{simple_complex3.eps}
-\end{center}
-\end{figure*}
 
@@
 
+\bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay, 
+\& Cs{\'a}nyi}{2011}]{dnest} {\bf Brewer B.~J.}, P{\'a}rtay L.~B., Cs{\'a}nyi G., 2011, Diffusive Nested Sampling, 
+Statistics and Computing, 21, 4, 649-656.
+
 \bibitem[\protect\citeauthoryear{Brewer et al.}{2012}]{2012arXiv1201.1677B} 

### 2012-08-29 MakeFigures/simple_complex1.py
Removing old figures that I no longer want

@@ -1,31 +1,0 @@
-from numpy import *
-from matplotlib.pyplot import *
-from scipy.optimize import fmin
-matplotlib.rcParams['font.size'] = 14
-matplotlib.rcParams['legend.fontsize'] = 14
-
-def chisq(params):
-	global x, y_complex
-	m = params[0]
-	b = params[1]
-	y_simple = m*x + b
-	return trapz((y_simple - y_complex)**2, x=x)
-
-x = linspace(-5.0, 5.0, 301)
-y_complex = x + sin(2*pi*x/4.0) - 0.15*x**2
-params = array([0.0, 0.0]) # Initial guess for straight line
-params = fmin(chisq, params)
-m = params[0]
-b = params[1]
-y_simple = m*x + b
-
-plot(x, y_complex, label='Complex Reality')
-plot(x, y_simple, 'r', label='Simple Model Fit')
-xlabel('x')
-ylabel('y')
-legend(loc='upper left')
-
-savefig('simple_complex1.eps')
-
-show()
-

### 2012-08-29 MakeFigures/simple_complex2.py

@@ -1,39 +1,0 @@
-from numpy import *
-from matplotlib.pyplot import *
-from scipy.optimize import fmin
-import matplotlib
-matplotlib.rcParams['font.size'] = 14
-matplotlib.rcParams['legend.fontsize'] = 14
-
-def negative_entropy(params):
-	global x, y_complex
-	mu = params[0]
-	lamb = params[1]
-	nu = params[2]
-	y_simple = (1.0 + lamb*(x - mu)**2/nu)**(-(nu + 1)/2.0)
-	y_simple = y_simple/trapz(y_simple, x=x)
-	return trapz(y_complex*log(y_complex/y_simple), x=x)
-
-x = linspace(-5.0, 5.0, 301)
-y_complex = exp(-abs(x/0.3)) + 0.3*exp(-0.5*((x-1.0)/0.5)**2)
-y_complex = y_complex/trapz(y_complex, x=x)
-params = array([0.0, 1.0, 5.0]) # Initial guess for t distribution parameters
-			   # location, precision, degrees of freedom
-params = fmin(negative_entropy, params)
-mu = params[0]
-lamb = params[1]
-nu = params[2]
-y_simple = (1.0 + lamb*(x - mu)**2/nu)**(-(nu + 1)/2.0)
-y_simple = y_simple/trapz(y_simple, x=x)
-
-plot(x, y_complex, label='Complex Reality')
-plot(x, y_simple, 'r', label='Simple Model Fit')
-xlabel('x')
-ylabel('y')
-legend(loc='upper left')
-print(params)
-
-savefig('simple_complex2.eps')
-
-show()
-

### 2012-08-29 MakeFigures/simple_complex3.py

@@ -1,46 +1,0 @@
-from numpy import *
-from matplotlib.pyplot import *
-from scipy.optimize import fmin
-import matplotlib
-matplotlib.rcParams['font.size'] = 14
-matplotlib.rcParams['legend.fontsize'] = 14
-
-def negative_entropy(params):
-	global x, y, z_complex
-	mu_x = params[0]
-	mu_y = params[1]
-	sig = params[2]
-	z_simple = exp(-0.5*((x - mu_x)**2 + (y - mu_y)**2)/sig**2)
-	z_simple = z_simple/z_simple.sum()
-	return sum(z_complex*log(z_complex/z_simple))
-
-x = linspace(-4.0, 4.0, 101)
-y = linspace(-4.0, 4.0, 101)
-[x, y] = meshgrid(x, y)
-y = -y
-
-component1 = exp(-sqrt(x**2 + ((y+1)/0.5)**2))
-component1 = component1/component1.sum()
-component2 = exp(-0.5*((x - 1.0)**2 + (y - 0.5)**2))
-component2 = component2/component2.sum()
-
-z_complex = 0.5*component1 + 0.5*component2
-
-params = array([0.0, 0.0, 1.0]) # Initial guess for gaussian parameters
-			        # [mu_x, mu_2, sig]
-params = fmin(negative_entropy, params)
-mu_x = params[0]
-mu_y = params[1]
-sig = params[2]
-z_simple = exp(-0.5*((x - mu_x)**2 + (y - mu_y)**2)/sig**2)
-z_simple = z_simple/z_simple.sum()
-
-imshow(z_complex, extent = [-4.0, 4.0, -4.0, 4.0])
-contour(x, y, z_simple, 10, colors="white")
-xlabel('x')
-ylabel('y')
-
-savefig('simple_complex3.eps')
-show()
-
-

### 2012-08-29 Code/Emission_Line/FitLine.cpp
log-Uniform prior on sigma boost

@@ -37,7 +37,7 @@ void FitLine::fromPrior()
 	A = exp(log(1E-3) + log(1E6)*randomU());
 	c = -10. + 20.*randomU();
 	w = exp(log(1E-3) + log(1E6)*randomU());
-	sigmaBoost = exp(5*randn());
+	sigmaBoost = exp(log(1E-3) + log(1E6)*randomU());
 }
 
 double FitLine::perturb()
@@ -67,9 +67,8 @@ double FitLine::perturb()
 	else
 	{
 		sigmaBoost = log(sigmaBoost);
-		logH -= -0.5*pow(sigmaBoost/5., 2);
-		sigmaBoost += 5.*pow(10., 1.5 - 6.*randomU())*randn();
-		logH += -0.5*pow(sigmaBoost/5., 2);
+		sigmaBoost += log(1E6)*pow(10., 1.5 - 6.*randomU())*randn();
+		sigmaBoost = mod(sigmaBoost - log(1E-3), log(1E6)) + log(1E-3);
 		sigmaBoost = exp(sigmaBoost);
 	}
 

### 2012-08-29 Code/Emission_Line/display.py
Save fluxes

@@ -26,3 +26,5 @@ plt.hist(flux, 30)
 print((flux.mean(), flux.std(), (flux.mean() - 1.)/flux.std()))
 plt.show()
 
+np.savetxt('flux.txt', flux)
+

### 2012-08-29 ms.tex
Results from fit

@@
 \end{eqnarray}
+We ran this model through DNest and found that it also does not work. The
+true value of $F$ is 1, and the inferred values of $F$ are
+$(0.9401 \pm 0.0072)$ and $(0.9404 \pm 0.0083)$
+respectively. The true value is an $8.3-\sigma$ outlier from the posterior
+using the simple model, and this is only reduced to $7.2-\sigma$ by the
+inclusion of the ``sigma-boost'' parameter $\kappa$. Clearly this is an
+unsatisfactory situation.
 

### 2012-08-29 ms.tex
Results numbers fixed

--- 2012-08-29 ms.tex
@@
 \end{eqnarray}
+We ran this model through DNest and found that it also does not work. The
+true value of $F$ is 1, and the inferred values of $F$ (posterior mean
+$\pm$ posterior standard deviation) are
+$(0.9407 \pm 0.0044)$ and $(0.9402 \pm 0.0077)$
+respectively. The true value is a $13.5$-$\sigma$ outlier from the posterior
+using the simple model, and this is only reduced to $7.7$-$\sigma$ by the
+inclusion of the ``sigma-boost'' parameter $\kappa$. Clearly this is an
+unsatisfactory situation.
 

### 2012-08-31 Code/Emission_Line/plot_hists.py
New failure plot

@@ -3,15 +3,16 @@ from pylab import *
 flux1 = loadtxt('flux1.txt')
 flux2 = loadtxt('flux2.txt')
 
-hist(flux1, 20, normed=True, histtype='step', label='$\\sigma$-boost included', linewidth=2)
-hist(flux2, 20, normed=True, histtype='step', label='$\\sigma$-boost not included', color='r', linewidth=2)
+hist(flux1, 20, normed=True, histtype='step', label='$\\sigma$-boost not included', linewidth=2)
+hist(flux2, 20, normed=True, histtype='step', label='$\\sigma$-boost included', color='r', linewidth=2)
 xlim([0.9, 1.1])
 ylim([0, 120])
 plot([1, 1], [0, 120], 'k--', linewidth=2, label='True Value')
 legend()
 xlabel('Total Flux', fontsize=14)
 ylabel('Posterior Probability', fontsize=14)
+savefig('../../failure.eps')
 show()
 
-savefig('../../failure.eps')
+
 

### 2012-08-31 ms.tex
Convergence plot in paper
Failure plot in paper
Gregory reference
Figure labels
Approximating the pdf

@@
 
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.5]{failure.eps}
+\caption{\label{failure}}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.5]{convergence.eps}
+\caption{\label{convergence}}
+\end{center}
+\end{figure*}
+
 \begin{itemize}
@@
 \section{More Objective Temperature Selection}
+Suppose the complex model has parameters $\eta$.
+The joint prior between the simple model parameters $\theta$ and the data $D$
+is given by:
+\begin{eqnarray}
+q_0(\theta, D).
+\end{eqnarray}
+We wish to approximate this by another distribution:
+\begin{eqnarray}
+p_T(\theta, D) &=& p(\theta)\mathcal{L}(\theta; D).
+\end{eqnarray}
+This approximation will be done by maximising:
+\begin{eqnarray}
+H(T) &=& -\int p_T(\theta, D) \log q_0(\theta, D) \, d\theta \, dD
+\end{eqnarray}
+
 \begin{itemize}
@@
 
+\bibitem[Gregory(2005)]{gregory} Gregory, P.~C., 2005, 
+Bayesian Logical Data Analysis for the Physical Sciences. Cambridge 
+University Press.\
+
 \bibitem[\protect\citeauthoryear{Jaynes 

### 2013-04-06 ms.tex
Fixed typo
Some random writing ont he plane

@@
 \newcommand{\yy}{\mathbf{y}}
+\newcommand{\dnest}{\texttt{DNest}}
 
@@
 \begin{abstract}
-We discuss the practical use of simply parameterised models in Bayesian data analysis, particularly in astronomy.
-The use of simply parameterised models is problematic when they are fit to large, informative data sets, resulting in unrealistically small uncertainties on inferences.
+We discuss the practical use of simply parameterised models in Bayesian data analysis.
+These models can be problematic when they are fit to large, informative data sets, resulting in unrealistically small uncertainties on the resulting inferences.
 In common parlance, the formal statistical errors may be small, but the systematic errors are often large and in many cases, difficult to quantify at all.
@@
 The key idea is to weaken the connection between the parameters and the data that is assumed in the prior probabilities.
-This weakening can be implemented straightforwardly using the Nested Sampling algorithm.
+This weakening can be implemented straightforwardly after-the-fact using the Nested Sampling algorithm.
 \end{abstract}
@@
 When the number of parameters being inferred is 3 or greater, enumeration of
-all possible values becomes computationally prohibitive. In this situation,
+all possible values and their probabilities becomes computationally prohibitive.
+In this situation,
 Markov Chain Monte Carlo (MCMC) methods are commonly used to produce samples
@@
 + 5\exp\left[-\frac{1}{2}\left(\frac{x + 1}{0.5}\right)^2\right]
-%M = 3*exp(-0.5*(x/0.3)**2) + exp(-0.5*(x-1.)**2) + 5*exp(-0.5*((x+1)/0.5)**2)
+\label{eqn:truth}
 \end{eqnarray}
@@
 \end{eqnarray}
-To simulate noise in the measurement process, errors $\{\epsilon_i\}$ were added, generated
+To simulate noise in the measurement process, errors $\{\epsilon_i\}$ were
+added, generated
 independently from a normal distribution with mean 0 and standard deviation
@@
 \end{eqnarray}
-The simulated data is shown in Figure~\ref{emission_line}.
+The simulated noisy data is shown in Figure~\ref{emission_line}.
 
@@
 complex model), it does not make much sense to look at the posterior distribution
-for the parameters. However, consider the total flux:
+for them. However, consider the total flux:
 \begin{eqnarray}
@@
 This can be computed both for the true underlying complex model, and the fitted
-simple models. In other words, it ``exists''. We computed the posterior distribution
+simple models. In simpler terms, it ``exists''. We computed the posterior distribution
 for the total flux using the posterior samples. These are plotted in
@@
 \end{eqnarray}
-We ran this model through DNest and found that it also does not work. The
+We ran this model through \dnest and found that it also does not work. The
 true value of $F$ is 1, and the inferred values of $F$ (posterior mean
@@
 \end{figure*}
+
+\section{Simply-Parameterised Model Parameters Exist}
+Consider our emission line example. The true underlying function was given
+in Equation~\ref{eqn:truth}. Now imagine that we had a family of simply
+parameterised models $M(x)$, parameterised by $\theta$:
+\begin{eqnarray}
+M(x; \theta)
+\end{eqnarray}
+Suppose we wanted to, for summary purposes, describe the complex truth
+$\mathcal{M}_0(x)$ by some fitted simple model that maximises the following:
+\begin{eqnarray}
+S(\theta) &=& \int \mathcal{M}_0(x)\log\left(M(x; \theta)\right) \, dx
+\end{eqnarray}
+subject to the constraint of equal normalisations:
+\begin{eqnarray}
+\int M(x) \, dx = \int \mathcal{M}_0(x) \, dx
+\end{eqnarray}
 

### 2013-04-06 ms.tex
Random attempts

@@
 \section{More Objective Temperature Selection}
-Suppose the complex model has parameters $\eta$.
-The joint prior between the simple model parameters $\theta$ and the data $D$
-is given by:
+Suppose the complex model has parameters $\xi$ and the simple model
+has parameters $\theta$. What we really want is the posterior for $\theta$:
 \begin{eqnarray}
-q_0(\theta, D).
+p(\theta|x) \propto p(\theta)p(x|\theta)
 \end{eqnarray}
-We wish to approximate this by another distribution:
+But the likelihood $p(x|\theta)$ is unavailable. All we have access to is the
+likelihood given {\it complex} model parameters, that is, we can evaluate
+$p(x|\xi)$. For the purposes of predicting data, $\xi$ makes $\theta$
+redundant:
 \begin{eqnarray}
-p_T(\theta, D) &=& p(\theta)\mathcal{L}(\theta; D).
+p(x|\xi) = p(x|\xi, \theta)
 \end{eqnarray}
-This approximation will be done by maximising:
+
+Suppose we can also sample the joint distribution between $\xi$, $\theta$
+and $x$.
 \begin{eqnarray}
-H(T) &=& -\int p_T(\theta, D) \log q_0(\theta, D) \, d\theta \, dD
+p(\xi)p(\theta|\xi)p(x|\theta, \xi) &=& p(\xi)\delta\left(
+\theta - f(\xi)\right)p(x|\xi)
 \end{eqnarray}
+This implies the following joint distribution for $\theta$ and $x$:
+\begin{eqnarray}
+p(\theta, x) &=& \int p(\xi)\delta\left(
+\theta - f(\xi)\right)p(x|\xi) \, d\xi
+\end{eqnarray}
+
+We shall approximate our target posterior with things we can actually
+implement, and then optimise our approximation. Adding subscripts to the target
+posterior:
+\begin{eqnarray}
+p_0(\theta|x) \propto p_0(\theta)p_0(x|\theta).
+\end{eqnarray}
+
+%The joint prior between the simple model parameters $\theta$ and the data $x$
+%is given by:
+%\begin{eqnarray}
+%p_0(\theta, x) &=& \int p_0(\xi, \theta, x) \, d\xi \\
+%&=& \int p_0(\xi)p_0(\theta|\xi)p_0(x|\theta, \xi) \, d\xi \\
+%&=& \int p_0(\xi)\delta\left(\theta - f(\xi)\right)p_0(x|\theta, \xi) \, d\xi \\
+%&=& \int p_0(\xi)\delta\left(\theta - f(\xi)\right)p_0(x|\theta, \xi) \, d\xi
+%\end{eqnarray}
+%We wish to approximate this by another distribution:
+%\begin{eqnarray}
+%p_T(\theta, D) &=& p(\theta)\mathcal{L}(\theta; D).
+%\end{eqnarray}
+%This approximation will be done by maximising:
+%\begin{eqnarray}
+%H(T) &=& -\int p_T(\theta, D) \log q_0(\theta, D) \, d\theta \, dD
+%\end{eqnarray}
 

### 2013-08-10 MakeFigures/joint.py
New figure

@@ -1,0 +1,80 @@
+from pylab import *
+
+"""
+Plot an illustrative joint prior implied by a complex
+model, and then the same thing implied by a simple model.
+"""
+
+x = linspace(-10, 10, 201)
+y = linspace(-10, 10, 201)
+[x, y] = meshgrid(x, y)
+y = y[::-1, :]
+
+px = exp(-0.5*x**2)
+for i in xrange(0, x.shape[1]):
+	px[i, :] /= px[i, :].sum() 
+
+pyx  = x.copy()
+for i in xrange(0, x.shape[1]):
+	pyx[:,i] = exp(-0.5*(y[:,i] - x[:,i])**2)
+	pyx[:,i] /= pyx[:,i].sum()
+
+joint = px*pyx
+pxy = joint.copy()
+for i in xrange(0, y.shape[0]):
+	pxy[i, :] = joint[i, :]/joint[i, :].sum()
+
+subplot(2,3,1)
+imshow(joint, extent=[-10, 10, -10, 10])
+xlabel('$\\theta$')
+ylabel('$x$')
+title('$p(\\theta, x)$')
+
+subplot(2,3,2)
+imshow(pyx, extent=[-10, 10, -10, 10])
+xlabel('$\\theta$')
+ylabel('$x$')
+title('$p(x|\\theta)$')
+
+subplot(2,3,3)
+imshow(pxy, extent=[-10, 10, -10, 10])
+xlabel('$\\theta$')
+ylabel('$x$')
+title('$p(\\theta|x)$')
+
+px = exp(-0.5*x**2/3**2)
+for i in xrange(0, x.shape[1]):
+	px[i, :] /= px[i, :].sum() 
+
+pyx  = x.copy()
+for i in xrange(0, x.shape[1]):
+	pyx[:,i] = exp(-0.5*(y[:,i] - x[:,i])**2/0.3**2)
+	pyx[:,i] /= pyx[:,i].sum()
+
+joint = px*pyx
+pxy = joint.copy()
+for i in xrange(0, y.shape[0]):
+	pxy[i, :] = joint[i, :]/joint[i, :].sum()
+
+subplot(2,3,4)
+imshow(joint, extent=[-10, 10, -10, 10])
+xlabel('$\\theta$')
+ylabel('$x$')
+title('$p(\\theta, x)$')
+
+subplot(2,3,5)
+imshow(pyx, extent=[-10, 10, -10, 10])
[…]

### 2013-08-10 SandBox/ms.tex
Notes

\documentclass[a4paper, 11pt]{article}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage[left=3cm,top=3cm,right=3cm]{geometry}

\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\parindent=0cm

%\title{Document Title}
%\author{Brendon J. Brewer}

\begin{document}
%\maketitle

The complex model implies a joint prior
\begin{eqnarray}
p_c(\theta, x) = p_c(\theta)p_c(x|\theta) = p_c(x)p_c(\theta|x).
\end{eqnarray}

The simple model implies its own joint prior
\begin{eqnarray}
p_s(\theta, x) = p_s(\theta)p_s(x|\theta) = p_s(x)p_s(\theta|x).
\end{eqnarray}

We would like to get the posterior under the complex model, $p_c(\theta|x)$,
but that might be too hard.
We wouldn't really mind if we could compute the results with the
simple model's prior. This would give a posterior
\begin{eqnarray}
p(\theta | x) \propto p_s(\theta)p_c(x|\theta).
\end{eqnarray}
but we can't compute that either because $p_c(x|\theta)$ is intractable.

One distribution for $\theta$ that we can compute is the following:
\begin{eqnarray}
q_\eta(\theta | x) \propto p_s(\theta)\mathcal{L}_\eta(\theta; x).
\end{eqnarray}
Here $\mathcal{L}$ is some scalar that quantifies the match between $\theta$ and
$x$ and it also depends on adjustable parameter(s) $\eta$. A concrete example
would be saying that $\mathcal{L}_\eta(\theta; x) = p_s(x|\theta)^{1/\eta}$, i.e.
using a tempered version of the simple model's likelihood function.
The expected score (with a logarithmic scoring rule) when using this approximating
distribution is
\begin{eqnarray}
\int p_c(\theta | x) \log q_\eta(\theta | x) \, d\theta
\end{eqnarray}
and we want to choose the value of $\eta$ that maximises this.

Alright, I'll now bite the bullet. Optimising the expected score, given the data,
is hard. What if we optimise the pre-data expected score? This is
\begin{eqnarray}
\iint p_c(x) p_c(\theta | x) \log q_\eta(\theta | x) \, d\theta \, dx
\end{eqnarray}

\end{document}

### 2013-08-27 SandBox/ms.tex
Z

@@
 \end{eqnarray}
+The normalised version of this distribution is
+\begin{eqnarray}
+q_\eta(\theta | x) &=& \frac{p_s(\theta)\mathcal{L}_\eta(\theta; x)}
+{\mathcal{Z}(\eta; x)}
+\end{eqnarray}
+where $\mathcal{Z}(\eta; x) = \int p_s(\theta)\mathcal{L}_\eta(\theta; x) \, d\theta$.
+
 Here $\mathcal{L}$ is some scalar that quantifies the match between $\theta$ and
@@
 \begin{eqnarray}
-\int p_c(\theta | x) \log q_\eta(\theta | x) \, d\theta
+\int p_c(\theta | x) \log q_\eta(\theta | x) \, d\theta\\
+&=& \int q_\eta(\theta | x) \frac{p_c(\theta | x)}{q_\eta(\theta | x)} \log q_\eta(\theta | x) \, d\theta
 \end{eqnarray}
@@
 
-Alright, I'll now bite the bullet. Optimising the expected score, given the data,
-is hard. What if we optimise the pre-data expected score? This is
-\begin{eqnarray}
-\iint p_c(x) p_c(\theta | x) \log q_\eta(\theta | x) \, d\theta \, dx
-\end{eqnarray}
+%We could do a MaxEnt type approximation, which IMO is not correct here because
+%the constraint is only an approximation and not legitimate information. But it
+%might be tractable.
 

### 2013-12-28 ms2.tex
New document

--- 2012-08-31 ms.tex
@@
-\documentclass[letterpaper, 11pt]{article}
+\documentclass[a4paper, 11pt]{article}
 \usepackage{authblk}	% For nice author-affil lists
@@
 \newcommand{\yy}{\mathbf{y}}
+\newcommand{\dnest}{\texttt{DNest}}
 
-\title{Reliable Inferences from Simply Parameterised Models}
+\title{Inferring Macroscopic Properties}
 
-\author[1,2]{Brendon J. Brewer}
-\author[3]{Geraint~F.~Lewis}
-\author[4]{Ross Fadely}
-\affil[1]{\small Dept. of Physics, University of California, Santa Barbara, CA 93106, USA}
-\affil[2]{Department of Statistics, University of Auckland, Private Bag 92019, Auckland, New Zealand
-}
-\affil[3]{Sydney Institute for Astronomy, School of Physics, The University of Sydney, A28, Sydney, 2006, Australia}
-\affil[4]{Department of Astronomy, Haverford College, 370 Lancaster Ave., Haverford, PA 19041 USA}
+\author[1]{Brendon J. Brewer}
+\affil[1]{Department of Statistics, University of Auckland, Private Bag 92019, Auckland, New Zealand}
 
@@
 \begin{abstract}
-We discuss the practical use of simply parameterised models in Bayesian data analysis, particularly in astronomy.
-The use of simply parameterised models is problematic when they are fit to large, informative data sets, resulting in unrealistically small uncertainties on inferences.
-In common parlance, the formal statistical errors may be small, but the systematic errors are often large and in many cases, difficult to quantify at all.
-In principle, the best solution to this problem is to develop more realistic complex models that accurately describe our prior beliefs.
-However, this is often infeasible in practice, due to computational limitations and the difficulty of defining satisfactory prior distributions over high dimensional spaces.
-As a pragmatic alternative, we show that it is possible to reinterpret the use of simple models in a way that avoids the problem of overconfident
-inferences.
-The key idea is to weaken the connection between the parameters and the data that is assumed in the prior probabilities.
-This weakening can be implemented straightforwardly using the Nested Sampling algorithm.
 \end{abstract}
@@
 \section{Introduction}
-
-Bayesian Inference is a powerful framework for modelling uncertainty that has
-been successfully applied in many scientific fields. The basic idea
-is that we can model the degree of plausibility of a hypothesis $H$ by a real
-number in $[0, 1]$, and that these numbers should be manipulated according to
-the rules of probability theory. If we are initially uncertain about some
-hypothesis $H$, we model this as a {\it prior probability} $P(H)$. If some other
-hypothesis $D$ is discovered to be true, the plausibility of $H$ is updated to
-the {\it posterior probability} using Bayes' rule:
-\begin{equation}
-P(H|D) = \frac{P(H)P(D|H)}{P(D)}
-\end{equation}
-
-One common application of Bayesian Inference is for parameter estimation.
-Suppose there is some quantity $\theta$ that is unknown. Initially, we describe
-our uncertainty by a prior probability distribution $p(\theta)$. We also know about some
-observation or experiment that will yield data $D$ that will provide some
-information about $\theta$. We describe our knowledge about this process by a 
-set of conditional probability distributions $p(D|\theta)$. Then, once a specific data set
-$D_{\rm obs}$ has been observed, we update our state of knowledge about $\theta$
-to the {\it posterior distribution}:
-\begin{equation}
-p(\theta | D) \propto p(\theta) p(D|\theta)|_{D=D_{\rm obs}}
-\end{equation}
-The various terms in this equation have the following names and meanings.
-
-\begin{itemize}
-\item $p(\theta|D)$ is the {\it posterior distribution}
-for the parameters, and is usually the goal of the calculation. It describes our
-knowledge and remaining uncertainty about $\theta$ after taking into account the data. \\
-
-\item $p(\theta)$ is the {\it prior distribution}, a probability distribution
-over possible values for $\theta$ that describes our uncertainty about
-$\theta$ before taking into account the data. In many applications, this is a broad
-probability distribution describing a large amount of uncertainty. \\
-
-\item $p(D|\theta)$ is a function of
-both $\theta$ and $D$ and is sometimes referred to as the {\it sampling distribution}.
-Another name is the generative model. 
-The sampling distribution $p(D|\theta)$ is a set of probability distributions,
-one for each value of $\theta$, and describe our prior information about how the data are connected to the parameters \citep{2008arXiv0808.0012C}. In particular, it is the probability distribution
-for the data we might observe, {\it if} we knew the true value of the parameters
-$\theta$, as a function of $\theta$.
-
-\item $p(D|\theta)|_{D = D_{\rm obs}}$ is called the {\it likelihood function}.
-It is obtained from the sampling distribution, with the actual data substituted in,
-and is therefore a function of $\theta$ only. It describes the effects of the actual data
-set that was observed on our beliefs about $\theta$: values of $\theta$ with a high
-likelihood predicted the data well and will have their probability upweighted
-in the posterior distribution.
-\end{itemize}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=0.5]{joint_marginal.eps}
-\end{center}
-\end{figure*}
-
-When the number of parameters being inferred is 3 or greater, enumeration of
-all possible values becomes computationally prohibitive. In this situation,
-Markov Chain Monte Carlo (MCMC) methods are commonly used to produce samples
-drawn from the posterior distribution. These samples can then be used to view
-the marginal distribution for any particular parameter(s) of interest.
-In addition, if the
-samples are viewed as a movie, they can give the viewer an intuitive sense of
-the uncertainty in the determination of the parameters: any feature of the
-models that varies between movie frames is a conclusion that is uncertain, and any
-feature that is common to all frames in the movie is a feature that has a high
-posterior probability.
-
-{\bf Discuss the various attempts at robustness/model checking/elicitation and that stuff}
-
-\section{Two Kinds of Model}
-In this paper we consider two general categories of models that can be fit to
-data. The first of these we will call ``simply-parameterised'' models.
-
-\subsection{Simply-Parameterised Models}
-Simply-parameterised models, which are also
-commonly known as parametric models, are in widespread use for a number of reasons.
-Firstly, they are easy to implement in software, and sometimes analytical
-solutions are available for the inference of their parameters from data.
-Secondly, their parameters usually have simple meanings that are easy to interpret.
-This property makes communication easy, as well as making it straightforward to
-make uncontroversial prior probability
-assignments to the possible values of the parameters. Finally, when the inference
-is done computationally, the MCMC methods tend to work very well.
-
-\subsection{Complex Models}
-The second category of models we consider are ``complex'' models. These tend to
-be much more flexible and contain large numbers of unknown parameters. Complex
-models are often incorrectly referred to as nonparametric models. A better term
-would be flexible models or free-form models. The primary advantage of complex models is realism. The universe is not
-simple place, and it is rare that a physical situation can be described accurately
-by a simply-parameterised model which is often a simple mathematical formula.
-
-\section{An Example: Fitting an Emission Line}
-Throughout this paper we will use a simple example of fitting an emission line
-to noisy data to explore the properties of simply parameterised models. The
-simulated data was generated from the following complex model:
-\begin{eqnarray}
-\mathcal{M}_0(x) \propto 3\exp\left[-\frac{1}{2}\left(\frac{x}{0.3}\right)^2\right]
-+ \exp\left[-\frac{1}{2}\left(\frac{x - 1}{1}\right)^2\right]
-+ 5\exp\left[-\frac{1}{2}\left(\frac{x + 1}{0.5}\right)^2\right]
-%M = 3*exp(-0.5*(x/0.3)**2) + exp(-0.5*(x-1.)**2) + 5*exp(-0.5*((x+1)/0.5)**2)
-\end{eqnarray}
-The fluxes were evaluated at $x$-values ranging from $-10$ to $10$ in steps
-of $0.001$, and then normalised to sum to 1:
-\begin{eqnarray}
-\sum_{i=1}^N \mathcal{M}_0(x_i) &=& 1.
-\end{eqnarray}
-To simulate noise in the measurement process, errors $\{\epsilon_i\}$ were added, generated
-independently from a normal distribution with mean 0 and standard deviation
-$\sigma = 3 \times 10^{-4}$.
-This produces noisy data $\mathbf{y} = \{y_1, y_2, ..., y_N\}$:
-\begin{eqnarray}
-\begin{array}{lccr}
-y_i = \mathcal{M}_0(x_i) + \epsilon_i, & & & \epsilon_i \sim \mathcal{N}(0, \sigma^2).
-\end{array}
-\end{eqnarray}
-The simulated data is shown in Figure~\ref{emission_line}.
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=0.5]{emission_line.eps}
-\end{center}
-\caption{The simulated data that will be used to illustrate the properties of
-simply-parameterised models. {\bf Top}: The noise-free true model $\mathcal{M}_0(x)$,
-generated from a mixture of three Gaussians, and normalised to a sum of 1.
-{\bf Bottom}: Simulated data with added noise.\label{emission_line}}
-\end{figure*}
-
-\section{Fitting a Simply-Parameterised Model}
-We now explore what happens when we fit simulated data (bottom panel of
-Figure~\ref{emission_line}) with an inflexible simply-parameterised model.
-We will fit the data with single Gaussian component.
-The model for the shape of the line is:
-\begin{eqnarray}
-\mathcal{M}(x; A, c, w) &=&
-A\exp
-\left[
--\frac{1}{2w^2}
-\left(x - c\right)^2
-\right]
-\end{eqnarray}
-where $A$ is the peak amplitude, $c$ is the central position of the line
-and $w$ is the line width. To infer the parameters $\{A, c, w\}$ from some data
-$\yy = \{y_1, y_2, ..., y_N\}$, we will use Bayes' rule:
-\begin{eqnarray}
-p(A, c, w | \yy) \propto p(A, c, w)p(\yy | A, c, w).
-\end{eqnarray}
-To proceed, we just need to define the prior and the sampling distribution.
-
-\subsection{The Sampling Distribution}
-We will assume that the data are simply noisy measurements of the true line shape
-$\mathcal{M}(x)$ at a finite number of $x$-values.
-The sampling distribution, aka the probability distribution for the data $\yy$ given
-the parameters, is simply a normal/gaussian distribution. Note that the
-gaussian error assumption should be distinguished from the assumption of a gaussian
-shape for the emission line.
-
-\begin{eqnarray}
-p(\yy|A, c, w) &=& \prod_{i=1}^N
-\frac{1}{\sigma\sqrt{2\pi}}
-\exp
-\left[
--\frac{1}{2\sigma^2}\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2
-\right] \\
-&\propto& \exp\left[-\frac{1}{2\sigma^2}\sum_{i=1}^N\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2\right] \\
-&\propto& \exp\left[-\frac{1}{2}\chi^2({\tt model}, {\tt data})\right].
-\end{eqnarray}
-The likelihood here is related to the commonly used $\chi^2$ deviation between
-te model and the data.
-
-\subsection{The Prior Distribution}
-To proceed with the inference, we require a prior distribution over the space
-of possible parameter values for $A$, $c$ and $w$. We shall assume independence:
-\begin{eqnarray}
-p(A, c, w) = p(A)p(c)p(w).
-\end{eqnarray}
-This means that, prior to learning the data, we are unaware of any logical
-connection between the values of the parameters. In other words, if we learned the
-value of any parameter we would not update our knowledge about the others.
-For the central position $c$ of the line, we assigned a uniform prior between
-$-10$ and $10$, which is the same range as the data. For $A$ and $w$ we assigned
-priors proportional to $1/A$ and $1/w$ between $10^{-3}$ and $10^{+3}$, since these
-parameters are known to be positive and have an uncertain magnitude.
-
-\subsection{The Failure of the Simply Parameterised Model}
-We ran the simply parameterised model on the simulated data using the Diffusive
-Nested Sampling algorithm \citep{dnest}
-\footnote{A C++ implementation of Diffusive Nested Sampling is available
-online at {\tt http://github.com/eggplantbren/DNest3/}.}. This provides samples
-from the posterior distribution for the parameters $A$, $c$ and $w$. Since these
-parameters do not ``exist'' in reality (i.e. the data were generated from the
-complex model), it does not make much sense to look at the posterior distribution
-for the parameters. However, consider the total flux:
-\begin{eqnarray}
-F = \sum_{i=1}^N \mathcal{M}(x_i)
-\end{eqnarray}
-This can be computed both for the true underlying complex model, and the fitted
-simple models. In other words, it ``exists''. We computed the posterior distribution
-for the total flux using the posterior samples. These are plotted in
-Figure~\ref{failure}.
-
-A commonly suggested technique \citep[e.g.][]{gregory} to avoid this situation
-is to add an ``error-bar boost'' parameter which we will call $\kappa$.
-This adds one more parameter to the list, and the likelihood becomes:
-\begin{eqnarray}
-p(\yy|A, c, w, \kappa) &=& \prod_{i=1}^N
-\frac{1}{(\kappa\sigma)\sqrt{2\pi}}
-\exp
-\left[
--\frac{1}{2(\kappa\sigma)^2}\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2
-\right] \\
-&\propto& \kappa^{-N}\exp\left[-\frac{1}{2(\kappa\sigma)^2}\sum_{i=1}^N\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2\right]
-\end{eqnarray}
-We ran this model through DNest and found that it also does not work. The
-true value of $F$ is 1, and the inferred values of $F$ (posterior mean
-$\pm$ posterior standard deviation) are
-$(0.9407 \pm 0.0044)$ and $(0.9402 \pm 0.0077)$
-respectively. The true value is a $13.5$-$\sigma$ outlier from the posterior
-using the simple model, and this is only reduced to $7.7$-$\sigma$ by the
-inclusion of the ``sigma-boost'' parameter $\kappa$. Clearly this is an
-unsatisfactory situation.
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=0.5]{failure.eps}
-\caption{\label{failure}}
-\end{center}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=0.5]{convergence.eps}
-\caption{\label{convergence}}
-\end{center}
-\end{figure*}
-
-\begin{itemize}
-\item Easy to implement \\
-\item Computationally fast to get inferences - therefore can be applied on a large scale, e.g. to large samples of objects. \\
-\item Easy to assign non-controversial priors over low dimensional parameter spaces \\
-\end{itemize}
-
-\section{Problems with Simply Parameterised Models}
-\begin{itemize}
-\item They are usually false, i.e. poor models of our actual prior beliefs. \\
-\item Conditional on the simple model, you get error bars that are much too small.
-Small error bars on the parameters may not matter so much (since the parameters don't ``exist'' anyway), but the inferences on quantities that do ``exist'' (e.g.
-total flux) will still be overconfident.
-\\
-\end{itemize}
-
-\section{Re-Interpreting Simply Parameterised Models}
-
-\begin{itemize}
-\item Describe the hypothetical process of acknowledging the complex reality, yet describing (summarising) it by fitting a simple model to the complex one. \\
-\item Show some examples of this - complex curves being approximated by lines with least squares, complex density profiles (1-D and 2-D) being fit by simple density profiles by maximising some kind of entropy.
-\item Mention/derive that in the special case of fitting a complex density profile with a Gaussian, the variance(s) of the Gaussian gives the actual moment(s) of the complex profile
-\item Describe how fitting a simple model can be interpreted as attempting to infer the parameters of the summarising simple model, and that therefore the parameter space is completely legitimate - it's the likelihood function that is now wrong.
-Data = model predictions + noise breaks down, it should be Data = simple model predictions + complexity perturbations + noise
-\item Describe why qualitatively, the likelihood function should now be ``weaker'' than before
-\item Describe why the old likelihood function is still (often) a good hill to climb
-\end{itemize}
-
-\section{Implementation with Nested Sampling}
-\begin{itemize}
-\item Describe the concept of tempering/annealing and how it almost does what we want \\
-\item But we don't really know what temperature we want at the outset - NS allows us to test all in a single run
-\item Introduce ``convergence plots'' and how to read them
-\item Subjective temperature selection and why it's not so bad
-\end{itemize}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=0.7]{nested.eps}
-\end{center}
-\end{figure*}
-
-\section{More Objective Temperature Selection}
-Suppose the complex model has parameters $\eta$.
-The joint prior between the simple model parameters $\theta$ and the data $D$
-is given by:
-\begin{eqnarray}
-q_0(\theta, D).
-\end{eqnarray}
-We wish to approximate this by another distribution:
-\begin{eqnarray}
-p_T(\theta, D) &=& p(\theta)\mathcal{L}(\theta; D).
-\end{eqnarray}
-This approximation will be done by maximising:
-\begin{eqnarray}
-H(T) &=& -\int p_T(\theta, D) \log q_0(\theta, D) \, d\theta \, dD
-\end{eqnarray}
-
-\begin{itemize}
-\item If we can generate from a prior over complex models, and then fit simple models to each sample, and also generate simulated data from the complex model, we can get an idea of the joint prior over the space of (simple parameters, data)\\
-\item Approximate the joint prior over (simple parameters, data) with a tempered version of the old likelihood \\
-\item Find the optimal temperature that makes the approximated joint prior as close as possible to the true one.
-\end{itemize}
-
-\section{Failure Modes}
-\begin{itemize}
-\item If the simple model / original likelihood function is SO BAD that optimising it takes you to the wrong place in parameter space
-\end{itemize}
-
-\section{Simple Example 1: A rotation curve}
-
-\section{Simple Example 2: An emission line}
-
-\section{Potential Applications}
-
-\begin{itemize}
-\item Interferometry: a common goal of interferometry is to measure the angular size of some astronomical object, when it is too small to be resolved by standard telescopes.
-In the case of stellar interferometry, the surface brightness profile of a star is very well modelled by a circular disc with limb darkening, so this model should be used.
-However, with other objects, such as the dust torii in active galactic nuclei \citep[e.g.][]{2011A&A...536A..78K}, the spatial profile is not well known.
-If a characteristic size, or total flux or something, is the goal of the study, then the framework of this paper is applicable.\\
-
-\item Gravitational lensing: Modelling of gravitational lenses typically aims to infer the source surface brightness profile along with the projected mass density profile of the deflector.
-While sophisticated many-parameter models are feasible and are used routinely now \citep{2006MNRAS.371..983S, 2007ApJ...666..726B, 2011MNRAS.412.2521B, 2006ApJ...637..608B, 2012Natur.481..341V}, they are slow, and some are not particularly realistic anyway (rant about ``regularisation'' here).
-With the explosion in the number of known gravitational lens systems (ref?), population-based studies will need something faster.
-I have already used this approach \citep{2012arXiv1201.1677B}.
-
-\item Galaxy Structure and Morphology: Studies of populations of galaxies are often carried out by fitting simple models such as the S{\'e}rsic \citep{Sersic1968} profile to individual galaxies.
-It has been demonstrated that taking into account the full uncertainties on these parameters can yield different results as compared to simply studying the distribution of the best-fit parameters \citep[e.g.][]{2011MNRAS.414.1625Y}.
-However, since galaxies often are not well modelled by S{\'e}rsic profiles (due to their real-world complexity), the error bars on the parameters can be severely underestimated, which is almost like just using the best-fit parameters!
-\\
-
-\item Studying spectra: Measuring equivalent widths, velocity dispersions and so on from emission/absorption lines.
-These commonly assume a specific functional form for the spectral line profile (e.g.
-Gaussian), which may not be applicable.
-
-\item Any situation with correlated noise (but a believed model), we can use this method as well (e.g. \citep{2008ApJ...686..851R}).
-
-\item Ideas? There are surely a large number of possibilities
-\end{itemize}
+A hypothesis space indexed by parameters
+$\mathbf{x} = \{x_1, x_2, ..., x_n\}$. A macroscopic quantity
+is defined by a scalar function $f(\mathbf{x})$.
 
